---
title: "Analysis of computational modeling results"
author: "Milena Musial"
output: html_document
date: '2023-12-18'
format: 
  html:
    embed-resources: true
    toc: true
    toc-depth: 3
    code-fold: true
    number-sections: true
    fig-width: 8
    fig-height: 6
    fig-format: svg
    editor_options: 
    chunk_output_type: console
---

# Setup

```{r}
rm(list=ls())
libs<-c("tidyverse", "rstan", "gdata", "bayesplot", "stringr", "dplyr", "ggplot2", "loo", "hBayesDM", "lme4", "sjPlot", "ggpubr", "tidyr", "gmodels")
sapply(libs, require, character.only=TRUE)

data_path<-"/Users/milenamusial/Library/CloudStorage/OneDrive-Charité-UniversitätsmedizinBerlin/PhD/04_B01/ILT/WP2_ILT_DATA/Stan_Output/PH_withC"
project_path <- "/Users/milenamusial/Library/CloudStorage/OneDrive-Charité-UniversitätsmedizinBerlin/PhD/04_B01/ILT"

load(file.path(project_path, "WP2_ILT_DATA/RedCap/redcap_n58_new.RData"))

params <- read.table(file.path(data_path, 'Params_PH_withC_init05_n58.txt'), header = T)
PEs <- read.table(file.path(data_path, 'fmri_PEs_PH_withC_init05_n58.txt'), header = T)
CPs <- read.table(file.path(data_path, 'fmri_pcs_PH_withC_init05_n58.txt'), header = T)
Qs <- read.table(file.path(data_path, 'fmri_Qs_PH_withC_init05_n58.txt'), header = T)

```

```{r}
# prepare params df
params <- params %>%
  select(!ID_block) %>%
  mutate(ID = as.factor(ID),
         aud_group = as.factor(aud_group),
         reinforcer_type = as.factor(reinforcer_type),
         block = as.factor(block))

# prepare trial-by-trial df
trialy_by_trial_df <- left_join(PEs, CPs, by = c("ID_block", "trial_block", "reinforcer_type", "ID"))
trialy_by_trial_df <- left_join(trialy_by_trial_df, Qs, by = c("ID_block", "trial_block", "reinforcer_type", "ID"))
trialy_by_trial_df <- trialy_by_trial_df %>%
  select(ID, reinforcer_type, trial_block, PE_pred, pc_pred, Q_pred)

trialy_by_trial_df <- trialy_by_trial_df %>%
  mutate(ID = as.factor(ID),
         reinforcer_type = as.factor(reinforcer_type))

trialy_by_trial_df <- left_join(trialy_by_trial_df, redcap_new, by="ID")

# get p correct per block and aud group and trial for plotting
df_tbt_time <- trialy_by_trial_df %>%
  group_by(aud_group,reinforcer_type,trial_block) %>%
  dplyr::summarise(mean_PE = mean(abs(PE_pred), na.rm = TRUE),
            ci_l_PE = ci(abs(PE_pred), na.rm=TRUE)[2],
            ci_u_PE = ci(abs(PE_pred), na.rm=TRUE)[3],
            mean_CP = mean(pc_pred, na.rm = TRUE),
            ci_l_CP = ci(pc_pred, na.rm=TRUE)[2],
            ci_u_CP = ci(pc_pred, na.rm=TRUE)[3],
            mean_Q = mean(Q_pred, na.rm = TRUE),
            ci_l_Q = ci(Q_pred, na.rm=TRUE)[2],
            ci_u_Q = ci(Q_pred, na.rm=TRUE)[3],
  )

# set contrasts
contrasts(params$reinforcer_type) <- abs(contr.treatment(2)-1)
contrasts(trialy_by_trial_df$reinforcer_type) <- abs(contr.treatment(2)-1)
contrasts(df_tbt_time$reinforcer_type) <- abs(contr.treatment(2)-1)

contrasts(params$aud_group) <- abs(contr.treatment(2)-1)
contrasts(trialy_by_trial_df$aud_group) <- abs(contr.treatment(2)-1)
contrasts(df_tbt_time$aud_group) <- abs(contr.treatment(2)-1)
```

# Bayesian parameter analysis

```{r}
# posterior_draws <- extract(fit, pars = c("A_sub_m", "tau_sub_m", "gamma_sub_m", "C_sub_m", "A_sub_con_m", "tau_sub_con_m", "gamma_sub_con_m", "C_sub_con_m"))
# 
# HDIofMCMC(posterior_draws$A_sub_m)
# HDIofMCMC(posterior_draws$tau_sub_m)
# HDIofMCMC(posterior_draws$gamma_sub_m)
# HDIofMCMC(posterior_draws$C_sub_m)
# HDIofMCMC(posterior_draws$A_sub_con_m)
# HDIofMCMC(posterior_draws$tau_sub_con_m)
# HDIofMCMC(posterior_draws$gamma_sub_con_m)
# HDIofMCMC(posterior_draws$C_sub_con_m)
# 
# plotHDI(posterior_draws$A_sub_m)
# plotHDI(posterior_draws$tau_sub_m)
# plotHDI(posterior_draws$gamma_sub_m)
# plotHDI(posterior_draws$C_sub_m)
# plotHDI(posterior_draws$A_sub_con_m)
# plotHDI(posterior_draws$tau_sub_con_m)
# plotHDI(posterior_draws$gamma_sub_con_m)
# plotHDI(posterior_draws$C_sub_con_m)
```
# Computational parameters

## Alpha

```{r}
fig1 <- ggplot(params, aes(x = reinforcer_type, y = alpha, fill = reinforcer_type)) +
  geom_violin() +
  geom_boxplot(width=0.1, size=0.8) +
  facet_wrap(~aud_group, scales="fixed") +
  scale_y_continuous("Initial learning rate (α)", limits = c(0,1)) +
  theme_light(base_size=18) +
  theme(axis.title.x=element_blank(),
      axis.text.x=element_blank(),
      axis.ticks.x=element_blank(),
      legend.position = "bottom") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent")

fig1
```

```{r}
m_alpha <- lm(alpha ~ 1 + reinforcer_type*aud_group, data=params)

tab_model(m_alpha,
          dv.labels=c("m_correct"), digits=3, digits.re=2,
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))
```

We cannot include reinforcer type as random effect as the model would be unidentifiable. Therefore, the model only includes a random intercept.


## Inverse temperature

```{r}
fig2 <- ggplot(params, aes(x = reinforcer_type, y = tau, fill = reinforcer_type)) +
  geom_violin() +
  geom_boxplot(width=0.1, size=0.8) +
  facet_wrap(~aud_group, scales="fixed") +
  scale_y_continuous("Inverse temperature (β)", limits = c(0,100)) +
  theme_light(base_size=18) +
  theme(axis.title.x=element_blank(),
      axis.text.x=element_blank(),
      axis.ticks.x=element_blank(),
      legend.position = "bottom") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent")

fig2
```

```{r}
m_invtemp <- lm(tau ~ 1 + reinforcer_type*aud_group, data=params)

tab_model(m_invtemp,
          dv.labels=c("m_invtemp"), digits=3, digits.re=2,
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))
```

We cannot include reinforcer type as random effect as the model would be unidentifiable. Therefore, the model only includes a random intercept.

## Gamma

```{r}
fig3 <- ggplot(params, aes(x = reinforcer_type, y = gamma, fill = reinforcer_type)) +
  geom_violin() +
  geom_boxplot(width=0.1, size=0.8) +
  facet_wrap(~aud_group, scales="fixed") +
  scale_y_continuous("Decay constant (γ)", limits = c(0,1)) +
  theme_light(base_size=18) +
  theme(axis.title.x=element_blank(),
      axis.text.x=element_blank(),
      axis.ticks.x=element_blank(),
      legend.position = "bottom") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent")

fig3
```

```{r}
m_gamma <- lm(gamma ~ 1 + reinforcer_type*aud_group, data=params)

tab_model(m_gamma,
          dv.labels=c("m_gamma"), digits=3, digits.re=2,
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))
```

## C

```{r}
fig4 <- ggplot(params, aes(x = reinforcer_type, y = C, fill = reinforcer_type)) +
  geom_violin() +
  geom_boxplot(width=0.1, size=0.8) +
  facet_wrap(~aud_group, scales="fixed") +
  scale_y_continuous("Scaling coefficient (C)", limits = c(0,1)) +
  theme_light(base_size=18) +
  theme(axis.title.x=element_blank(),
      axis.text.x=element_blank(),
      axis.ticks.x=element_blank(),
      legend.position = "bottom") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent")

fig4
```

```{r}
m_C <- lm(C ~ 1 + reinforcer_type*aud_group, data=params)

tab_model(m_C,
          dv.labels=c("m_C"), digits=3, digits.re=2,
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))
```

We cannot include reinforcer type as random effect as the model would be unidentifiable. Therefore, the model only includes a random intercept.

## Combined plot

```{r}
# save combined plot
fig_params <- ggarrange(fig1, fig2, fig3, fig4,
          labels = c("A", "B", "C", "D"),
          ncol = 4, nrow = 1,
          common.legend = TRUE, legend="bottom")
fig_params

png("params.png", width = 24, height = 10, units='cm', res = 600)
fig_params
dev.off()
```

# Trial-by-trial quantities

## Absolute prediction errors

```{r}
fig_PE_time <- ggplot(df_tbt_time, aes(x=trial_block, y=abs(mean_PE), group=reinforcer_type)) +
  geom_line(aes(color=reinforcer_type), linewidth=0.8) +
  geom_ribbon(aes(ymin = ci_l_PE, ymax = ci_u_PE, fill = reinforcer_type), alpha = 0.2) + 
  facet_wrap(~aud_group, scales="free_y") +
  scale_y_continuous("Absolute \n prediction errors", limits = c(0,1)) +
  scale_x_continuous(NULL) +
  theme_light(base_size=18) +
  theme(legend.position = "right") +
  scale_color_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent")

fig_PE_time

```

```{r}
m_PE=lmer(PE_pred~reinforcer_type*aud_group*trial_block + (1 + trial_block | ID),
                data=trialy_by_trial_df,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_PE,
          dv.labels=c("m_rt_trial"), digits=3, digits.re=2, transform = NULL, show.est = T, 
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

```

## Choice probabilities of chosen option

```{r}
fig_CP_time <- ggplot(df_tbt_time, aes(x=trial_block, y=mean_CP, group=reinforcer_type)) +
  geom_line(aes(color=reinforcer_type), linewidth=0.8) +
  geom_ribbon(aes(ymin = ci_l_CP, ymax = ci_u_CP, fill = reinforcer_type), alpha = 0.2) + 
  facet_wrap(~aud_group, scales="free_y") +
  scale_y_continuous("Choice probabilities \n of chosen option", limits = c(0,1)) +
  scale_x_continuous(NULL) +
  theme_light(base_size=18) +
  theme(legend.position = "right") +
  scale_color_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent")

fig_CP_time

```

```{r}
m_CP=lmer(pc_pred~reinforcer_type*aud_group*trial_block + (1 + trial_block | ID),
                data=trialy_by_trial_df,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_CP,
          dv.labels=c("m_rt_trial"), digits=3, digits.re=2, transform = NULL, show.est = T, 
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

```

## Q-values of chosen option

```{r}
fig_Q_time <- ggplot(df_tbt_time, aes(x=trial_block, y=mean_Q, group=reinforcer_type)) +
  geom_line(aes(color=reinforcer_type), linewidth=0.8) +
  geom_ribbon(aes(ymin = ci_l_Q, ymax = ci_u_Q, fill = reinforcer_type), alpha = 0.2) + 
  facet_wrap(~aud_group, scales="free_y") +
  scale_y_continuous("Q-values \n of chosen option", limits = c(0,1)) +
  scale_x_continuous("Trial") +
  theme_light(base_size=18) +
  theme(legend.position = "right") +
  scale_color_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent")

fig_Q_time

```

```{r}
m_Q=lmer(Q_pred~reinforcer_type*aud_group*trial_block + (1 + trial_block | ID),
                data=trialy_by_trial_df,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_Q,
          dv.labels=c("m_rt_trial"), digits=3, digits.re=2, transform = NULL, show.est = T, 
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

```

## Combined plot

```{r}
# save combined plot
fig_trialbytrial <- ggarrange(fig_PE_time, fig_CP_time, fig_Q_time,
          labels = c("A", "B", "C"),
          ncol = 1, nrow = 3,
          common.legend = TRUE, legend="bottom")
fig_trialbytrial

png(file.path(project_path, "Manuscript/Figures", "trial_by_trial.png"), width = 16, height = 22, units='cm', res = 600)
fig_trialbytrial
dev.off()
```