---
title: "Analysis of computational modeling results"
author: "Milena Musial"
output: html_document
date: '2023-12-18'
format: 
  html:
    embed-resources: true
    toc: true
    toc-depth: 3
    code-fold: true
    number-sections: true
    fig-width: 8
    fig-height: 6
    fig-format: svg
    editor_options: 
    chunk_output_type: console
execute:
  warning: false
  message: false
---

# Setup

```{r, echo=FALSE, results='hide'}
rm(list=ls())

#lapply(names(sessionInfo()$loadedOnly), require, character.only = TRUE)
#invisible(lapply(paste0('package:', names(sessionInfo()$otherPkgs)), detach, character.only=TRUE, unload=TRUE, force=TRUE))

libs<-c("tidyverse", "rstan", "gdata", "bayesplot", "stringr", "dplyr", "ggplot2", "loo", "hBayesDM", "lme4", "sjPlot", "ggpubr", "tidyr", "gmodels", "performance", "robustlmm", "lmerTest", "emmeans", "confintROB")
invisible(sapply(libs, require, character.only=TRUE))

data_path<-"/Users/milenamusial/Library/CloudStorage/OneDrive-Charité-UniversitätsmedizinBerlin/PhD/04_B01/ILT/WP2_ILT_DATA/Stan_Output/PH_withC"
project_path <- "/Users/milenamusial/Library/CloudStorage/OneDrive-Charité-UniversitätsmedizinBerlin/PhD/04_B01/ILT"

load(file.path(project_path, "WP2_ILT_DATA/RedCap/redcap_n58_new.RData"))
load(file.path(project_path, "WP2_ILT_DATA/Behav/behav_final_n58.RData"))
load(file.path(project_path, "WP2_ILT_DATA/Behav/behav_final_redcap_n58.RData"))

behav_final_redcap <- behav_final_redcap %>%
  rowwise() %>%
  mutate(taste = (taste1+taste2)/2,
         crave = (crave1+crave2)/2)

df_taste_crave <- behav_final_redcap %>%
  select(ID, reinforcer_type, taste, crave, BA_smoking_days) %>%
  unique()

params <- read.table(file.path(data_path, 'Params_PH_withC_init05_n58.txt'), header = T)
PEs <- read.table(file.path(data_path, 'fmri_PEs_PH_withC_init05_n58.txt'), header = T)
CPs <- read.table(file.path(data_path, 'fmri_pcs_PH_withC_init05_n58.txt'), header = T)
Qs <- read.table(file.path(data_path, 'fmri_Qs_PH_withC_init05_n58.txt'), header = T)

# number notation without exponentials
options(scipen = 50)

##### define se function #####

se <- function(x, na.rm = FALSE) {
  if (na.rm) {
    x <- x[!is.na(x)]       # remove NA, NaN, etc.
  }
  sd(x, na.rm = na.rm) / sqrt(length(x))
}
```

```{r}
### prepare params df ###

params <- params %>%
  select(!ID_block) %>%
  mutate(ID = as.factor(ID),
         aud_group = factor(aud_group, levels = c("HC", "AUD")),
         reinforcer_type = as.factor(reinforcer_type),
         block = as.factor(block))

params <- left_join(params, df_taste_crave)

### prepare trial-by-trial df ###

trialy_by_trial_df <- left_join(PEs, CPs, by = c("ID_block", "trial_block", "reinforcer_type", "ID"))
trialy_by_trial_df <- left_join(trialy_by_trial_df, Qs, by = c("ID_block", "trial_block", "reinforcer_type", "ID"))
trialy_by_trial_df <- trialy_by_trial_df %>%
  select(ID, reinforcer_type, trial_block, PE_pred, pc_pred, Q_pred) %>%
  mutate(ID = as.factor(ID),
         reinforcer_type = as.factor(reinforcer_type),
         abs_PE_pred = abs(PE_pred))

trialy_by_trial_df <- left_join(trialy_by_trial_df, behav_final_redcap, by=c("ID", "reinforcer_type", "trial_block"))
trialy_by_trial_df <- trialy_by_trial_df %>%
  select(ID, ID_block, aud_group, age, taste, crave, BA_smoking_days, reinforcer_type, trial_block, choice, PE_pred, abs_PE_pred, pc_pred, Q_pred) %>%
  mutate(aud_group = factor(aud_group, levels = c("HC", "AUD"))) %>%
  arrange(ID_block)

# rearrange NAs in trial-by-trial quantities to be at position where no choice was made

new_PEs_all <- c()
new_absPEs_all <- c()
new_CPs_all <- c()
new_Qs_all <- c()

for (n in 1:length(unique(trialy_by_trial_df$ID_block))) {
  
  id <- unique(trialy_by_trial_df$ID_block)[n]
  
  # get original vectors
  choices <- trialy_by_trial_df$choice[trialy_by_trial_df$ID_block==id]
  PEs <- trialy_by_trial_df$PE_pred[trialy_by_trial_df$ID_block==id]
  absPEs <- trialy_by_trial_df$abs_PE_pred[trialy_by_trial_df$ID_block==id]
  CPs <- trialy_by_trial_df$pc_pred[trialy_by_trial_df$ID_block==id]
  Qs <- trialy_by_trial_df$Q_pred[trialy_by_trial_df$ID_block==id]
  
  # initialize new sorted vectors
  PEs_new <- PEs
  absPEs_new <- absPEs
  CPs_new <- CPs
  Qs_new <- Qs
  
  # find indices where choice is NA
  na_indices <- which(is.na(choices))
  
  # shift values forward and fill NA where choice is NA
  for (i in seq_along(na_indices)) {
  
    PEs_new[(na_indices[i]+1):length(PEs_new)] <- PEs_new[na_indices[i]:(length(PEs_new)-1)]  
    PEs_new[na_indices[i]] <- NA
    PEs_new <- PEs_new[1:length(PEs)]
    
    absPEs_new[(na_indices[i]+1):length(absPEs_new)] <- absPEs_new[na_indices[i]:(length(absPEs_new)-1)]  
    absPEs_new[na_indices[i]] <- NA
    absPEs_new <- absPEs_new[1:length(absPEs)]
    
    CPs_new[(na_indices[i]+1):length(CPs_new)] <- CPs_new[na_indices[i]:(length(CPs_new)-1)]  
    CPs_new[na_indices[i]] <- NA
    CPs_new <- CPs_new[1:length(CPs)]
    
    Qs_new[(na_indices[i]+1):length(Qs_new)] <- Qs_new[na_indices[i]:(length(Qs_new)-1)]  
    Qs_new[na_indices[i]] <- NA
    Qs_new <- Qs_new[1:length(Qs)]
    
  }
  
  new_PEs_all <- append(new_PEs_all, PEs_new)
  new_absPEs_all <- append(new_absPEs_all, absPEs_new)
  new_CPs_all <- append(new_CPs_all, CPs_new)
  new_Qs_all <- append(new_Qs_all, Qs_new)
  
}

trialy_by_trial_df$new_PEs <- new_PEs_all
trialy_by_trial_df$new_absPEs <- new_absPEs_all
trialy_by_trial_df$new_CPs <- new_CPs_all
trialy_by_trial_df$new_Qs <- new_Qs_all

# df per block and aud group and trial for plotting
df_tbt_time <- trialy_by_trial_df %>%
  group_by(aud_group,reinforcer_type,trial_block) %>%
  dplyr::summarise(mean_PE = mean(new_absPEs, na.rm = TRUE),
            ci_l_PE = ci(new_absPEs, na.rm=TRUE)[2],
            ci_u_PE = ci(new_absPEs, na.rm=TRUE)[3],
            mean_CP = mean(new_CPs, na.rm = TRUE),
            ci_l_CP = ci(new_CPs, na.rm=TRUE)[2],
            ci_u_CP = ci(new_CPs, na.rm=TRUE)[3],
            mean_Q = mean(new_Qs, na.rm = TRUE),
            ci_l_Q = ci(new_Qs, na.rm=TRUE)[2],
            ci_u_Q = ci(new_Qs, na.rm=TRUE)[3],
  ) %>%
  mutate(aud_group = factor(aud_group, levels = c("HC", "AUD")))

# df per block and group for plotting 
df_tbt_average <- trialy_by_trial_df %>%
  group_by(aud_group,reinforcer_type) %>%
  dplyr::summarise(mean_PE = mean(new_absPEs, na.rm = TRUE),
            ci_l_PE = ci(new_absPEs, na.rm=TRUE)[2],
            ci_u_PE = ci(new_absPEs, na.rm=TRUE)[3],
            mean_CP = mean(new_CPs, na.rm = TRUE),
            ci_l_CP = ci(new_CPs, na.rm=TRUE)[2],
            ci_u_CP = ci(new_CPs, na.rm=TRUE)[3],
            mean_Q = mean(new_Qs, na.rm = TRUE),
            ci_l_Q = ci(new_Qs, na.rm=TRUE)[2],
            ci_u_Q = ci(new_Qs, na.rm=TRUE)[3],
  ) %>%
  mutate(aud_group = factor(aud_group, levels = c("HC", "AUD")))

# set contrasts

# contrasts(params$reinforcer_type) <- abs(contr.treatment(2)-1)
# contrasts(trialy_by_trial_df$reinforcer_type) <- abs(contr.treatment(2)-1)
# contrasts(df_tbt_time$reinforcer_type) <- abs(contr.treatment(2)-1)
# 
# contrasts(params$aud_group)
# contrasts(trialy_by_trial_df$aud_group)
# contrasts(df_tbt_time$aud_group)

contrasts(params$reinforcer_type) <- c(0.5, -0.5)
contrasts(trialy_by_trial_df$reinforcer_type) <- c(0.5, -0.5)
contrasts(df_tbt_time$reinforcer_type) <- c(0.5, -0.5)

contrasts(params$aud_group) <- c(-0.5, 0.5)
contrasts(trialy_by_trial_df$aud_group) <- c(-0.5, 0.5)
contrasts(df_tbt_time$aud_group) <- c(-0.5, 0.5)
```

# Computational parameters

## Alpha

### Descriptive stats

```{r}
stats <- params %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('alpha'), .fns=
                   list('_mean' = mean,
                        '_se' = se,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))
stats
```

```{r}
fig1 <- ggplot(params, aes(x = fct_rev(fct_infreq(reinforcer_type)), y = alpha, fill = reinforcer_type)) +
  geom_violin() +
  geom_boxplot(width=0.1, size=0.8) +
  facet_wrap(~aud_group, scales="fixed") +
  scale_x_discrete(NULL, labels=c("juice", "alcohol")) +
  scale_y_continuous("Initial learning rate (α)", limits = c(0,1)) +
  theme_light(base_size=18, base_family = "Aptos") +
  theme(legend.position = "none") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("juice", "alcohol"),
                  palette = "Pastel1")
fig1
```

### LMMs

```{r}
m_alpha <- lme4::lmer(alpha ~ 1 + reinforcer_type*aud_group + (1 | ID), 
                data=params,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_alpha,
          dv.labels=c("m_alpha"), digits=2, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

check_model(m_alpha, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))
```

```{r}
# robust estimation
m_alpha_robust <- rlmer(alpha ~ 1 + reinforcer_type*aud_group + (1 | ID), 
                        data=params,
                        control=lmerControl(calc.derivs=FALSE))

tab_model(m_alpha_robust,
          dv.labels=c("m_alpha_robust"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

# CIs <- confintROB(m_alpha_robust, parm=c(1:4), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_alpha_robust_ec.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_alpha_robust_ec.rds"))
CIs
```

### Controlling for covariates

#### Check correlation

```{r}
# taste
lm_alpha_taste <- lmer(alpha ~ taste + (1 | ID), 
                       data=params,
                       control=lmerControl(calc.derivs=FALSE))

tab_model(lm_alpha_taste,
          dv.labels=c("lm_alpha_taste"), digits=2, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

check_model(lm_alpha_taste, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

lm_alpha_taste_rob <- rlmer(alpha ~ taste + (1 | ID), 
                            data=params,
                            control=lmerControl(calc.derivs=FALSE))

tab_model(lm_alpha_taste_rob,
          dv.labels=c("lm_alpha_taste_rob"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

# CIs <- confintROB(lm_alpha_taste_rob, parm=c(1:2), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_alpha_taste_rob.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_alpha_taste_rob.rds"))
CIs

# smoking
lm_alpha_smoking <- lmer(alpha ~ BA_smoking_days + (1 | ID), 
                         data=params,
                         control=lmerControl(calc.derivs=FALSE))

tab_model(lm_alpha_smoking,
          dv.labels=c("lm_alpha_smoking"), digits=5, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

check_model(lm_alpha_smoking, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

lm_alpha_smoking_rob <- rlmer(alpha ~ BA_smoking_days + (1 | ID), 
                              data=params,
                              control=lmerControl(calc.derivs=FALSE))

tab_model(lm_alpha_smoking_rob,
          dv.labels=c("lm_alpha_smoking_rob"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

# CIs <- confintROB(lm_alpha_smoking_rob, parm=c(1:2), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_alpha_smoking_rob.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_alpha_smoking_rob.rds"))
CIs
```

No control needed.

## Inverse temperature

### Descriptive stats

```{r}
stats <- params %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('tau'), .fns=
                   list('_mean' = mean,
                        '_se' = se,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))
stats
```

```{r}
fig2 <- ggplot(params, aes(x = fct_rev(fct_infreq(reinforcer_type)), y = tau, fill = reinforcer_type)) +
  geom_violin() +
  geom_boxplot(width=0.1, size=0.8) +
  facet_wrap(~aud_group, scales="fixed") +
  scale_x_discrete(NULL, labels=c("juice", "alcohol")) +
  scale_y_continuous("Inverse temperature (β)", limits = c(0,100)) +
  theme_light(base_size=18, base_family = "Aptos") +
  theme(legend.position = "none") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Pastel1")

fig2
```

### LMMs

```{r}
m_invtemp <- lmer(tau ~ 1 + reinforcer_type*aud_group + (1 | ID), 
                  data=params,
                  control=lmerControl(calc.derivs=FALSE))

tab_model(m_invtemp,
          dv.labels=c("m_invtemp"), digits=2, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

check_model(m_invtemp, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

# robust estimation
m_invtemp_robust <- rlmer(tau ~ 1 + reinforcer_type*aud_group + (1 | ID), 
                          data=params,
                          control=lmerControl(calc.derivs=FALSE))

tab_model(m_invtemp_robust,
          dv.labels=c("m_invtemp"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

# CIs <- confintROB(m_invtemp_robust, parm=c(1:4), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_invtemp_robust_ec.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_invtemp_robust_ec.rds"))
CIs
```

### Controlling for covariates

#### Check correlation

```{r}
# taste
lm_invtemp_taste <- lmer(tau ~ taste + (1 | ID), 
                         data=params,
                         control=lmerControl(calc.derivs=FALSE))

tab_model(lm_invtemp_taste,
          dv.labels=c("lm_invtemp_taste"), digits=2, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

check_model(lm_invtemp_taste, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

lm_invtemp_taste_rob <- rlmer(tau ~ taste + (1 | ID), 
                         data=params,
                         control=lmerControl(calc.derivs=FALSE))

tab_model(lm_invtemp_taste_rob,
          dv.labels=c("lm_invtemp_taste_rob"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

# CIs <- confintROB(lm_invtemp_taste_rob, parm=c(1:2), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_invtemp_taste_rob.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_invtemp_taste_rob.rds"))
CIs

# smoking
lm_invtemp_smoking <- lmer(tau ~ BA_smoking_days + (1 | ID), 
                         data=params,
                         control=lmerControl(calc.derivs=FALSE))

tab_model(lm_invtemp_smoking,
          dv.labels=c("lm_invtemp_smoking"), digits=2, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

check_model(lm_invtemp_smoking, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

lm_invtemp_smoking_rob <- rlmer(tau ~ BA_smoking_days + (1 | ID), 
                         data=params,
                         control=lmerControl(calc.derivs=FALSE))

tab_model(lm_invtemp_smoking_rob,
          dv.labels=c("lm_invtemp_smoking_rob"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

# CIs <- confintROB(lm_invtemp_smoking_rob, parm=c(1:2), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_invtemp_smoking_rob.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_invtemp_smoking_rob.rds"))
CIs

```

No control necessary.

## Gamma

### Descriptive stats

```{r}
stats <- params %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('gamma'), .fns=
                   list('_mean' = mean,
                        '_se' = se,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))
stats
```

```{r}
fig3 <- ggplot(params, aes(x = fct_rev(fct_infreq(reinforcer_type)), y = gamma, fill = reinforcer_type)) +
  geom_violin() +
  geom_boxplot(width=0.1, size=0.8) +
  facet_wrap(~aud_group, scales="fixed") +
  scale_x_discrete("Reinforcer type", labels=c("juice", "alcohol")) +
  scale_y_continuous("Decay constant (γ)", limits = c(0,1)) +
  theme_light(base_size=18, base_family = "Aptos") +
  theme(legend.position = "none") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Pastel1")

fig3
```

### LMMs

```{r}
m_gamma <- lmer(gamma ~ 1 + reinforcer_type*aud_group + (1 | ID), 
                data=params,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_gamma,
          dv.labels=c("m_gamma"), digits=5, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

check_model(m_gamma, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

# robust estimation
m_gamma_robust <- rlmer(gamma ~ 1 + reinforcer_type*aud_group + (1 | ID), 
                        data=params,
                        control=lmerControl(calc.derivs=FALSE))

tab_model(m_gamma_robust,
          dv.labels=c("m_gamma_robust"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

# CIs <- confintROB(m_gamma_robust, parm=c(1:4), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_gamma_robust_ec.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_gamma_robust_ec.rds"))
CIs
```

### Controlling for covariates

#### Check correlation

```{r}
# taste
lm_gamma_taste <- lmer(gamma ~ taste + (1 | ID), 
                         data=params,
                         control=lmerControl(calc.derivs=FALSE))

tab_model(lm_gamma_taste,
          dv.labels=c("lm_gamma_taste"), digits=5, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

check_model(lm_gamma_taste, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

lm_gamma_taste_rob <- rlmer(gamma ~ taste + (1 | ID), 
                         data=params,
                         control=lmerControl(calc.derivs=FALSE))

tab_model(lm_gamma_taste_rob,
          dv.labels=c("lm_gamma_taste_rob"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

# CIs <- confintROB(lm_gamma_taste_rob, parm=c(1:2), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_gamma_taste_rob.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_gamma_taste_rob.rds"))
CIs

# smoking
lm_gamma_smoking <- lmer(gamma ~ BA_smoking_days + (1 | ID), 
                         data=params,
                         control=lmerControl(calc.derivs=FALSE))

tab_model(lm_gamma_smoking,
          dv.labels=c("lm_gamma_smoking"), digits=5, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

check_model(lm_gamma_smoking, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

lm_gamma_smoking_rob <- rlmer(gamma ~ BA_smoking_days + (1 | ID), 
                         data=params,
                         control=lmerControl(calc.derivs=FALSE))

tab_model(lm_gamma_smoking_rob,
          dv.labels=c("lm_gamma_smoking_rob"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

# CIs <- confintROB(lm_gamma_smoking_rob, parm=c(1:2), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_gamma_smoking_rob.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_gamma_smoking_rob.rds"))
CIs

```

No control necessary.

## C

### Descriptive stats

```{r}
stats <- params %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('C'), .fns=
                   list('_mean' = mean,
                        '_se' = se,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))
stats
```

```{r}
fig4 <- ggplot(params, aes(x = fct_rev(fct_infreq(reinforcer_type)), y = C, fill = reinforcer_type)) +
  geom_violin() +
  geom_boxplot(width=0.1, size=0.8) +
  facet_wrap(~aud_group, scales="fixed") +
  scale_x_discrete("Reinforcer type", labels=c("juice", "alcohol")) +
  scale_y_continuous("Scaling coefficient (C)", limits = c(0,1)) +
  theme_light(base_size=18, base_family = "Aptos") +
  theme(legend.position = "none") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Pastel1")

fig4

```

### LMMs

```{r}
m_C <- lmer(C ~ 1 + reinforcer_type*aud_group + (1 | ID), 
            data=params,
            control=lmerControl(calc.derivs=FALSE))

tab_model(m_C,
          dv.labels=c("m_C"), digits=5, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

check_model(m_C, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

# robust estimation
m_C_robust <- rlmer(C ~ 1 + reinforcer_type*aud_group + (1 | ID), 
                    data=params,
                    control=lmerControl(calc.derivs=FALSE))

tab_model(m_C_robust,
          dv.labels=c("m_C_robust"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

# CIs <- confintROB(m_C_robust, parm=c(1:4), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_C_robust_ec.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_C_robust_ec.rds"))
CIs

```

### Controlling for covariates

#### Check correlation

```{r}
# taste
lm_C_taste <- lmer(C ~ taste + (1 | ID), 
                         data=params,
                         control=lmerControl(calc.derivs=FALSE))

tab_model(lm_C_taste,
          dv.labels=c("lm_C_taste"), digits=2, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

check_model(lm_C_taste, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

lm_C_taste_rob <- rlmer(C ~ taste + (1 | ID), 
                         data=params,
                         control=lmerControl(calc.derivs=FALSE))

tab_model(lm_C_taste_rob,
          dv.labels=c("lm_C_taste_rob"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

# CIs <- confintROB(lm_C_taste_rob, parm=c(1:2), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_C_taste_rob.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_C_taste_rob.rds"))
CIs

# smoking
lm_C_smoking <- lmer(C ~ BA_smoking_days + (1 | ID), 
                         data=params,
                         control=lmerControl(calc.derivs=FALSE))

tab_model(lm_C_smoking,
          dv.labels=c("lm_C_smoking"), digits=5, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

check_model(lm_C_smoking, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

lm_C_smoking_rob <- rlmer(C ~ BA_smoking_days + (1 | ID), 
                         data=params,
                         control=lmerControl(calc.derivs=FALSE))

tab_model(lm_C_smoking_rob,
          dv.labels=c("lm_C_smoking_rob"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

#CIs <- confintROB(lm_C_smoking_rob, parm=c(1:2), level=0.95, method="boot", boot.type = "parametric")
#saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_C_smoking_rob.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_C_smoking_rob.rds"))
CIs

```

No control necessary.

# Log likelihood

```{r}
df_log_likelihood <- trialy_by_trial_df %>%
  group_by(ID, aud_group, reinforcer_type, taste, crave, BA_smoking_days) %>%
  dplyr::summarise(log_likelihood = sum(log(pc_pred), na.rm=T))
```

### Descriptive stats

```{r}
stats <- df_log_likelihood %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('log_likelihood'), .fns=
                   list('_mean' = mean,
                        '_se' = se,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))
stats
```

```{r}
fig5 <- ggplot(df_log_likelihood, aes(x = fct_rev(fct_infreq(reinforcer_type)), y = log_likelihood, fill = reinforcer_type)) +
  geom_violin() +
  geom_boxplot(width=0.1, size=0.8) +
  facet_wrap(~aud_group, scales="fixed") +
  scale_x_discrete("Reinforcer type", labels=c("juice", "alcohol")) +
  scale_y_continuous("Log likelihood", limits = c(-40,0)) +
  theme_light(base_size=18, base_family = "Aptos") +
  theme(legend.position = "none") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Pastel1")

fig5
```

### LMMs

```{r}
m_ll <- lmer(log_likelihood ~ 1 + reinforcer_type*aud_group + (1 | ID), 
            data=df_log_likelihood,
            control=lmerControl(calc.derivs=FALSE))

tab_model(m_ll,
          dv.labels=c("m_ll"), digits=2, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

check_model(m_ll, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

# robust estimation
m_ll_robust <- rlmer(log_likelihood ~ 1 + reinforcer_type*aud_group + (1 | ID), 
            data=df_log_likelihood,
            control=lmerControl(calc.derivs=FALSE))

tab_model(m_ll_robust,
          dv.labels=c("m_ll_robust"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

# CIs <- confintROB(m_ll_robust, parm=c(1:4), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_ll_robust_ec.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_ll_robust_ec.rds"))
CIs

```

### Controlling for covariates

#### Check correlation

```{r}
# taste
lm_ll_taste <- lmer(log_likelihood ~ taste + (1 | ID), 
                         data=df_log_likelihood,
                         control=lmerControl(calc.derivs=FALSE))

tab_model(lm_ll_taste,
          dv.labels=c("lm_ll_taste"), digits=2, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

check_model(lm_ll_taste, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

lm_ll_taste_rob <- rlmer(log_likelihood ~ taste + (1 | ID), 
                         data=df_log_likelihood,
                         control=lmerControl(calc.derivs=FALSE))

tab_model(lm_ll_taste_rob,
          dv.labels=c("lm_ll_taste_rob"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

# CIs <- confintROB(lm_ll_taste_rob, parm=c(1:2), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_ll_taste_rob.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_ll_taste_rob.rds"))
CIs

# smoking
lm_ll_smoking <- lmer(log_likelihood ~ BA_smoking_days + (1 | ID), 
                         data=df_log_likelihood,
                         control=lmerControl(calc.derivs=FALSE))

tab_model(lm_ll_smoking,
          dv.labels=c("lm_ll_smoking"), digits=2, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

check_model(lm_ll_smoking, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

lm_ll_smoking_rob <- rlmer(log_likelihood ~ BA_smoking_days + (1 | ID), 
                         data=df_log_likelihood,
                         control=lmerControl(calc.derivs=FALSE))

tab_model(lm_ll_smoking_rob,
          dv.labels=c("lm_ll_smoking_rob"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=0.95,CSS = css_theme("cells"))

# CIs <- confintROB(lm_ll_smoking_rob, parm=c(1:2), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_ll_smoking_rob.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_ll_smoking_rob.rds"))
CIs
```

No controlling necessary.

# Combined plot

```{r}
# save combined plot
fig_param <- ggarrange(fig1, fig2, fig3, fig4,
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)
fig_param

fig_comp_mod <- ggarrange(fig_param, fig5,
          labels = c("A", "E"),
          ncol = 1, nrow = 2, heights = c(2, 1))
fig_comp_mod

#ggsave(file.path(project_path, "Manuscript/Initial_draft/Figures", "final_comp_modeling.png"), width = 20, height =25, units='cm', dpi = 1000, bg="white")
```
