---
title: "Demographic data"
author: "Milena Musial"
format:
  html:
    embed-resources: true
    editor: visual
    toc: true
    toc-depth: 4
    number-sections: true
    number-depth: 4
editor_options: 
  chunk_output_type: inline
---

# Preps

```{r}
rm(list=ls())

libs<-c("tidyverse", "stringr", "plyr", "dplyr", "lme4", "lmerTest","kableExtra", "gmodels", "sjPlot", "rstatix", "ggpubr")
sapply(libs, require, character.only=TRUE)

data_path<-'/Users/milenamusial/Library/CloudStorage/OneDrive-Charité-UniversitätsmedizinBerlin/PhD/04_B01/ILT/WP2_ILT_DATA/'

sample = "n56" # n58 n71 n13

if (sample == "n56") {
  load(file.path(data_path,"RedCap/redcap_n56_new.RData"))
} else if (sample == "n58") {
  load(file.path(data_path,"RedCap/redcap_n58_new.RData"))
} else if (sample == "n13") {
  load(file.path(data_path,"RedCap/redcap_n71_new.RData"))
  redcap_new_71 <- redcap_new
  load(file.path(data_path,"RedCap/redcap_n58_new.RData"))
  redcap_new_58 <- redcap_new
  redcap_new <- redcap_new_71[! redcap_new_71$ID %in% redcap_new_58$ID, ]
}

# rename
redcap <- redcap_new

# remove old variables
rm(list=(ls()[! ls()  %in% c("redcap", "data_path", "sample")]))
```

# Demographic variables

## Sex

```{r}
gender_summary <- redcap %>%
  select(aud_group, gender) %>%
  group_by(aud_group) %>%
  count()

gender_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}

test <- chisq.test(redcap$aud_group, redcap$gender)
print(test, digits=20)
```

## School degree

```{r}
graduat_summary <- redcap %>%
  select(aud_group, graduat) %>%
  group_by(aud_group) %>%
  count()

graduat_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
chisq.test(redcap$aud_group, redcap$graduat, simulate.p.value = T)
```

## Age

```{r}
age_summary <- redcap %>%
  select(aud_group, age) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(age, na.rm = TRUE),
                   sd_correct = sd(age, na.rm = TRUE),
                   min = min(age, na.rm = TRUE),
            max = max(age, na.rm = TRUE),
            ci_l = ci(age, na.rm = TRUE)[2],
            ci_u = ci(age, na.rm = TRUE)[3])

age_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")

print(age_summary$mean, digits=20)
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(age, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(age)
  
# normality
  redcap %>%
    select(age, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(age)
  ggqqplot(redcap, x = "age", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(age ~ aud_group)

### conduct test
t.test(redcap$age ~ redcap$aud_group, var.equal=T)
```

## Days between basic assessment and fMRI

```{r}
days_summary <- redcap %>%
  select(days_since_BA) %>%
  dplyr::summarise(mean = mean(days_since_BA, na.rm = TRUE),
                   sd_correct = sd(days_since_BA, na.rm = TRUE),
                   min = min(days_since_BA, na.rm = TRUE),
            max = max(days_since_BA, na.rm = TRUE),
            ci_l = ci(days_since_BA, na.rm = TRUE)[2],
            ci_u = ci(days_since_BA, na.rm = TRUE)[3])

days_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

# Psychometric variables

## AUD criteria

```{r}
aud_summary <- redcap %>%
  select(aud_group, aud_sum) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(aud_sum, na.rm = TRUE),
                   sd_correct = sd(aud_sum, na.rm = TRUE),
            min = min(aud_sum, na.rm = TRUE),
            max = max(aud_sum, na.rm = TRUE),
            ci_l = ci(aud_sum, na.rm = TRUE)[2],
            ci_u = ci(aud_sum, na.rm = TRUE)[3])

aud_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(aud_sum, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(aud_sum)
  
# normality
  redcap %>%
    select(aud_sum, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(aud_sum)
  ggqqplot(redcap, x = "aud_sum", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(aud_sum ~ aud_group)

### conduct test
wilcox.test(redcap$aud_sum ~ redcap$aud_group,
            exact = FALSE,
            correct = FALSE,
            conf.int = TRUE)
```

```{r}
fig_aud_crit <- ggplot(redcap, aes(x=as.factor(aud_sum))) +
  xlab("AUD criteria") +
  ylim(0,25) +
  geom_bar() +
  theme_minimal(base_size = 18) +
  scale_fill_brewer("Accent")
fig_aud_crit

ggsave(paste("/Users/milenamusial/Library/CloudStorage/OneDrive-Charité-UniversitätsmedizinBerlin/PhD/04_B01/ILT/Manuscript/Initial_draft/Figures/aud_criteria_", sample, ".png", sep=""), fig_aud_crit, width = 8, height = 5, dpi = 600)
```

## AUDIT

```{r}
audit_summary <- redcap %>%
  select(aud_group, MRI_audit_sum) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(MRI_audit_sum, na.rm = TRUE),
                   sd_correct = sd(MRI_audit_sum, na.rm = TRUE),
            min = min(MRI_audit_sum, na.rm = TRUE),
            max = max(MRI_audit_sum, na.rm = TRUE),
            ci_l = ci(MRI_audit_sum, na.rm = TRUE)[2],
            ci_u = ci(MRI_audit_sum, na.rm = TRUE)[3])

audit_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(MRI_audit_sum, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(MRI_audit_sum)
  
# normality
  redcap %>%
    select(MRI_audit_sum, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(MRI_audit_sum)
  ggqqplot(redcap, x = "MRI_audit_sum", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(MRI_audit_sum ~ aud_group)

### conduct test
t.test(redcap$MRI_audit_sum ~ redcap$aud_group, var.equal=FALSE)
```

## Drinking days past 3 months

```{r}
drinking_days_summary <- redcap %>%
  select(aud_group, BA_drinking_days) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(BA_drinking_days, na.rm = TRUE),
                   sd_correct = sd(BA_drinking_days, na.rm = TRUE),
            min = min(BA_drinking_days, na.rm = TRUE),
            max = max(BA_drinking_days, na.rm = TRUE),
            ci_l = ci(BA_drinking_days, na.rm = TRUE)[2],
            ci_u = ci(BA_drinking_days, na.rm = TRUE)[3])

drinking_days_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(BA_drinking_days, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(BA_drinking_days)
  
# normality
  redcap %>%
    select(BA_drinking_days, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(BA_drinking_days)
  ggqqplot(redcap, x = "BA_drinking_days", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(BA_drinking_days ~ aud_group)

### conduct test
wilcox.test(redcap$BA_drinking_days ~ redcap$aud_group,
            exact = FALSE,
            correct = FALSE,
            conf.int = TRUE)
```

## Drinks on drinking days past 3 months

```{r}
drinkstotal_summary <- redcap %>%
  select(aud_group, BA_drinks_past3months) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(BA_drinks_past3months, na.rm = TRUE),
                   sd_correct = sd(BA_drinks_past3months, na.rm = TRUE),
            min = min(BA_drinks_past3months, na.rm = TRUE),
            max = max(BA_drinks_past3months, na.rm = TRUE),
            ci_l = ci(BA_drinks_past3months, na.rm = TRUE)[2],
            ci_u = ci(BA_drinks_past3months, na.rm = TRUE)[3])

drinkstotal_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(BA_drinks_past3months, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(BA_drinks_past3months)
  
# normality
  redcap %>%
    select(BA_drinks_past3months, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(BA_drinks_past3months)
  ggqqplot(redcap, x = "BA_drinks_past3months", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(BA_drinks_past3months ~ aud_group)

### conduct test
t.test(redcap$BA_drinks_past3months ~ redcap$aud_group, var.equal=FALSE)
```

## Drinks weekday past 3 months

```{r}
drinksweekday_summary <- redcap %>%
  select(aud_group, BA_drinks_weekday) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(BA_drinks_weekday, na.rm = TRUE),
                   sd_correct = sd(BA_drinks_weekday, na.rm = TRUE),
            min = min(BA_drinks_weekday, na.rm = TRUE),
            max = max(BA_drinks_weekday, na.rm = TRUE),
            ci_l = ci(BA_drinks_weekday, na.rm = TRUE)[2],
            ci_u = ci(BA_drinks_weekday, na.rm = TRUE)[3])

drinksweekday_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(BA_drinks_weekday, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(BA_drinks_weekday)
  
# normality
  redcap %>%
    select(BA_drinks_weekday, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(BA_drinks_weekday)
  ggqqplot(redcap, x = "BA_drinks_weekday", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(BA_drinks_weekday ~ aud_group)

### conduct test
wilcox.test(redcap$BA_drinks_weekday ~ redcap$aud_group,
            exact = FALSE,
            correct = FALSE,
            conf.int = TRUE)
```

## Drinks weekend day past 3 months

```{r}
drinksweekendday_summary <- redcap %>%
  select(aud_group, BA_drinks_weekendday) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(BA_drinks_weekendday, na.rm = TRUE),
                   sd_correct = sd(BA_drinks_weekendday, na.rm = TRUE),
            min = min(BA_drinks_weekendday, na.rm = TRUE),
            max = max(BA_drinks_weekendday, na.rm = TRUE),
            ci_l = ci(BA_drinks_weekendday, na.rm = TRUE)[2],
            ci_u = ci(BA_drinks_weekendday, na.rm = TRUE)[3])

drinksweekendday_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(BA_drinks_weekendday, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(BA_drinks_weekendday)
  
# normality
  redcap %>%
    select(BA_drinks_weekendday, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(BA_drinks_weekendday)
  ggqqplot(redcap, x = "BA_drinks_weekendday", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(BA_drinks_weekendday ~ aud_group)

### conduct test
t.test(redcap$BA_drinks_weekendday ~ redcap$aud_group, var.equal=FALSE)
```

## Drinks past drinking occasion

```{r}
drinkspastoccasion_summary <- redcap %>%
  select(aud_group, BA_drinks_lastday) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(BA_drinks_lastday, na.rm = TRUE),
                   sd_correct = sd(BA_drinks_lastday, na.rm = TRUE),
            min = min(BA_drinks_lastday, na.rm = TRUE),
            max = max(BA_drinks_lastday, na.rm = TRUE),
            ci_l = ci(BA_drinks_lastday, na.rm = TRUE)[2],
            ci_u = ci(BA_drinks_lastday, na.rm = TRUE)[3])

drinkspastoccasion_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(BA_drinks_lastday, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(BA_drinks_lastday)
  
# normality
  redcap %>%
    select(BA_drinks_lastday, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(BA_drinks_lastday)
  ggqqplot(redcap, x = "BA_drinks_lastday", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(BA_drinks_lastday ~ aud_group)

### conduct test
t.test(redcap$BA_drinks_lastday ~ redcap$aud_group, var.equal=FALSE)
```

## Smoking days past 3 months

```{r}
smokingdays_summary <- redcap %>%
  select(aud_group, BA_smoking_days) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(BA_smoking_days, na.rm = TRUE),
                   sd_correct = sd(BA_smoking_days, na.rm = TRUE),
            min = min(BA_smoking_days, na.rm = TRUE),
            max = max(BA_smoking_days, na.rm = TRUE),
            ci_l = ci(BA_smoking_days, na.rm = TRUE)[2],
            ci_u = ci(BA_smoking_days, na.rm = TRUE)[3])

smokingdays_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(BA_smoking_days, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(BA_smoking_days)
  
# normality
  redcap %>%
    select(BA_smoking_days, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(BA_smoking_days)
  ggqqplot(redcap, x = "BA_smoking_days", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(BA_smoking_days ~ aud_group)

### conduct test
wilcox.test(redcap$BA_smoking_days ~ redcap$aud_group,
            exact = FALSE,
            correct = FALSE,
            conf.int = TRUE)
```

## CUD criteria

```{r}
can_summary <- redcap %>%
  select(aud_group, BA_can_sum) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(BA_can_sum, na.rm = TRUE),
                   sd_correct = sd(BA_can_sum, na.rm = TRUE),
            min = min(BA_can_sum, na.rm = TRUE),
            max = max(BA_can_sum, na.rm = TRUE),
            ci_l = ci(BA_can_sum, na.rm = TRUE)[2],
            ci_u = ci(BA_can_sum, na.rm = TRUE)[3])

can_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(BA_can_sum, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(BA_can_sum)
  
# normality
if (sample != "n13") {
  redcap %>%
    select(BA_can_sum, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(BA_can_sum)
}
  ggqqplot(redcap, x = "BA_can_sum", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(BA_can_sum ~ aud_group)
  
### conduct test
wilcox.test(redcap$BA_can_sum ~ redcap$aud_group,
            exact = FALSE,
            correct = FALSE,
            conf.int = TRUE)
```

## OCI total

```{r}
ocitotal_summary <- redcap %>%
  select(aud_group, oci_total) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(oci_total, na.rm = TRUE),
                   sd_correct = sd(oci_total, na.rm = TRUE),
            min = min(oci_total, na.rm = TRUE),
            max = max(oci_total, na.rm = TRUE),
            ci_l = ci(oci_total, na.rm = TRUE)[2],
            ci_u = ci(oci_total, na.rm = TRUE)[3])

ocitotal_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(oci_total, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(oci_total)
  
# normality
  redcap %>%
    select(oci_total, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(oci_total)
  ggqqplot(redcap, x = "oci_total", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(oci_total ~ aud_group)
  
### conduct test
t.test(redcap$oci_total ~ redcap$aud_group, var.equal=TRUE)
```

## COHS automaticity

```{r}
cohs_automaticity_summary <- redcap %>%
  select(aud_group, cohs_automaticity) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(cohs_automaticity, na.rm = TRUE),
                   sd_correct = sd(cohs_automaticity, na.rm = TRUE),
            min = min(cohs_automaticity, na.rm = TRUE),
            max = max(cohs_automaticity, na.rm = TRUE),
            ci_l = ci(cohs_automaticity, na.rm = TRUE)[2],
            ci_u = ci(cohs_automaticity, na.rm = TRUE)[3])

cohs_automaticity_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(cohs_automaticity, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(cohs_automaticity)
  
# normality
  redcap %>%
    select(cohs_automaticity, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(cohs_automaticity)
  ggqqplot(redcap, x = "cohs_automaticity", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(cohs_automaticity ~ aud_group)
  
### conduct test
t.test(redcap$cohs_automaticity ~ redcap$aud_group, var.equal=TRUE)
```

## COHS routine

```{r}
cohs_routine_summary <- redcap %>%
  select(aud_group, cohs_routine) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(cohs_routine, na.rm = TRUE),
                   sd_correct = sd(cohs_routine, na.rm = TRUE),
            min = min(cohs_routine, na.rm = TRUE),
            max = max(cohs_routine, na.rm = TRUE),
            ci_l = ci(cohs_routine, na.rm = TRUE)[2],
            ci_u = ci(cohs_routine, na.rm = TRUE)[3])

cohs_routine_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(cohs_routine, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(cohs_routine)
  
# normality
  redcap %>%
    select(cohs_routine, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(cohs_routine)
  ggqqplot(redcap, x = "cohs_routine", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(cohs_routine ~ aud_group)
  
### conduct test
t.test(redcap$cohs_routine ~ redcap$aud_group, var.equal=TRUE)
```

## UPPSP negative urgency

```{r}
uppsp_nu_summary <- redcap %>%
  select(aud_group, uppsp_negative_urgency) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(uppsp_negative_urgency, na.rm = TRUE),
                   sd_correct = sd(uppsp_negative_urgency, na.rm = TRUE),
            min = min(uppsp_negative_urgency, na.rm = TRUE),
            max = max(uppsp_negative_urgency, na.rm = TRUE),
            ci_l = ci(uppsp_negative_urgency, na.rm = TRUE)[2],
            ci_u = ci(uppsp_negative_urgency, na.rm = TRUE)[3])

uppsp_nu_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(uppsp_negative_urgency, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(uppsp_negative_urgency)
  
# normality
  redcap %>%
    select(uppsp_negative_urgency, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(uppsp_negative_urgency)
  ggqqplot(redcap, x = "uppsp_negative_urgency", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(uppsp_negative_urgency ~ aud_group)
  
### conduct test
t.test(redcap$uppsp_negative_urgency ~ redcap$aud_group, var.equal=TRUE)
```

## UPPSP premeditation

```{r}
uppsp_pre_summary <- redcap %>%
  select(aud_group, uppsp_premeditation) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(uppsp_premeditation, na.rm = TRUE),
                   sd_correct = sd(uppsp_premeditation, na.rm = TRUE),
            min = min(uppsp_premeditation, na.rm = TRUE),
            max = max(uppsp_premeditation, na.rm = TRUE),
            ci_l = ci(uppsp_premeditation, na.rm = TRUE)[2],
            ci_u = ci(uppsp_premeditation, na.rm = TRUE)[3])

uppsp_pre_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(uppsp_premeditation, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(uppsp_premeditation)
  
# normality
  redcap %>%
    select(uppsp_premeditation, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(uppsp_premeditation)
  ggqqplot(redcap, x = "uppsp_negative_urgency", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(uppsp_premeditation ~ aud_group)
  
### conduct test
t.test(redcap$uppsp_premeditation ~ redcap$aud_group, var.equal=FALSE)
```

## UPPSP perseverance

```{r}
uppsp_pers_summary <- redcap %>%
  select(aud_group, uppsp_perseverance) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(uppsp_perseverance, na.rm = TRUE),
                   sd_correct = sd(uppsp_perseverance, na.rm = TRUE),
            min = min(uppsp_perseverance, na.rm = TRUE),
            max = max(uppsp_perseverance, na.rm = TRUE),
            ci_l = ci(uppsp_perseverance, na.rm = TRUE)[2],
            ci_u = ci(uppsp_perseverance, na.rm = TRUE)[3])

uppsp_pers_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(uppsp_perseverance, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(uppsp_perseverance)
  
# normality
  redcap %>%
    select(uppsp_perseverance, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(uppsp_perseverance)
  ggqqplot(redcap, x = "uppsp_perseverance", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(uppsp_perseverance ~ aud_group)
  
### conduct test
t.test(redcap$uppsp_perseverance ~ redcap$aud_group, var.equal=TRUE)
```

## UPPSP sensation seeking

```{r}
uppsp_ss_summary <- redcap %>%
  select(aud_group, uppsp_sensation_seeking) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(uppsp_sensation_seeking, na.rm = TRUE),
                   sd_correct = sd(uppsp_sensation_seeking, na.rm = TRUE),
            min = min(uppsp_sensation_seeking, na.rm = TRUE),
            max = max(uppsp_sensation_seeking, na.rm = TRUE),
            ci_l = ci(uppsp_sensation_seeking, na.rm = TRUE)[2],
            ci_u = ci(uppsp_sensation_seeking, na.rm = TRUE)[3])

uppsp_ss_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(uppsp_sensation_seeking, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(uppsp_sensation_seeking)
  
# normality
  redcap %>%
    select(uppsp_sensation_seeking, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(uppsp_sensation_seeking)
  ggqqplot(redcap, x = "uppsp_sensation_seeking", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(uppsp_sensation_seeking ~ aud_group)
  
### conduct test
t.test(redcap$uppsp_sensation_seeking ~ redcap$aud_group, var.equal=TRUE)
```

## UPPSP positive urgency

```{r}
uppsp_pu_summary <- redcap %>%
  select(aud_group, uppsp_positive_urgency) %>%
  group_by(aud_group) %>%
  dplyr::summarise(mean = mean(uppsp_positive_urgency, na.rm = TRUE),
                   sd_correct = sd(uppsp_positive_urgency, na.rm = TRUE),
            min = min(uppsp_positive_urgency, na.rm = TRUE),
            max = max(uppsp_positive_urgency, na.rm = TRUE),
            ci_l = ci(uppsp_positive_urgency, na.rm = TRUE)[2],
            ci_u = ci(uppsp_positive_urgency, na.rm = TRUE)[3])

uppsp_pu_summary %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
### check assumptions
# outliers
  redcap %>%
    select(uppsp_positive_urgency, aud_group) %>%
    group_by(aud_group) %>%
    identify_outliers(uppsp_positive_urgency)
  
# normality
  redcap %>%
    select(uppsp_positive_urgency, aud_group) %>%
    group_by(aud_group) %>%
    shapiro_test(uppsp_positive_urgency)
  ggqqplot(redcap, x = "uppsp_positive_urgency", facet.by = "aud_group")
  
# homoscedasticity
  redcap %>%
    levene_test(uppsp_positive_urgency ~ aud_group)
  
### conduct test
t.test(redcap$uppsp_positive_urgency ~ redcap$aud_group, var.equal=FALSE)
```
