---
title: "02_Behavioral_Analyses"
author: "Milena Musial"
format:
  html:
    embed-resources: true
    editor: visual
    toc: true
    toc-depth: 4
    number-sections: true
    number-depth: 4
editor_options: 
  chunk_output_type: inline
---

# Preps

```{r}
rm(list=ls())

# load packages
libs<-c("tidyverse", "stringr", "plyr", "dplyr", "lme4", "robustlmm", "lmerTest",
        "sjPlot", "ggpubr", "gmodels", "PerformanceAnalytics", "car", "performance",
        "emmeans", "psych")
sapply(libs, require, character.only=TRUE)

#project_path <- "/Users/milenamusial/Library/CloudStorage/OneDrive-Charité-UniversitätsmedizinBerlin/PhD/04_B01/ILT"
project_path <- "/Users/milenamusial/Library/CloudStorage/OneDrive-Charité-UniversitätsmedizinBerlin/PhD/04_B01/ILT"

# define sample
sample <- "n58" # n71, n58, n56, n13

# load color
accent <- RColorBrewer::brewer.pal(7, "Accent")

if (sample == 'n71') {
  load(file.path(project_path, "WP2_ILT_DATA/Behav/behav_final_n71.RData"))
  load(file.path(project_path, "WP2_ILT_DATA/RedCap/redcap_n71_new.RData"))
  load(file.path(project_path, "WP2_ILT_DATA/Behav/behav_final_redcap_n71.RData"))
} else if (sample == 'n58') {
  load(file.path(project_path, "WP2_ILT_DATA/Behav/behav_final_n58.RData"))
  load(file.path(project_path, "WP2_ILT_DATA/RedCap/redcap_n58_new.RData"))
  load(file.path(project_path, "WP2_ILT_DATA/Behav/behav_final_redcap_n58.RData"))
} else if (sample == 'n56') {
  load(file.path(project_path, "WP2_ILT_DATA/Behav/behav_final_n56.RData"))
  load(file.path(project_path, "WP2_ILT_DATA/RedCap/redcap_n56_new.RData"))
  load(file.path(project_path, "WP2_ILT_DATA/Behav/behav_final_redcap_n56.RData"))
} else if (sample == 'n13') {
  load(file.path(project_path, "WP2_ILT_DATA/RedCap/redcap_n71_new.RData"))
  redcap_new_71 <- redcap_new
  load(file.path(project_path, "WP2_ILT_DATA/RedCap/redcap_n58_new.RData"))
  redcap_new_58 <- redcap_new
  redcap_new <- redcap_new_71[! redcap_new_71$ID %in% redcap_new_58$ID, ]
  load(file.path(project_path, "WP2_ILT_DATA/Behav/behav_final_n71.RData"))
  behav_final <- behav_final[behav_final$ID %in% redcap_new$ID, ]
  load(file.path(project_path, "WP2_ILT_DATA/Behav/behav_final_redcap_n71.RData"))
  behav_final_redcap <- behav_final_redcap[behav_final_redcap$ID %in% redcap_new$ID, ]
  rm(list = c("redcap_new_58", "redcap_new_71"))
}

redcap <- redcap_new

# create outcome as predictor for stay switch analyses
behav_final$outcome_pred <- factor(behav_final$outcome)
behav_final_redcap$outcome_pred <- factor(behav_final_redcap$outcome)

# set contrasts
contrasts(behav_final$reinforcer_type) <- abs(contr.treatment(2)-1)
contrasts(behav_final_redcap$reinforcer_type) <- abs(contr.treatment(2)-1)

redcap$aud_group <- factor(redcap$aud_group, levels = c("AUD", "HC"))
contrasts(redcap$aud_group) <- abs(contr.treatment(2)-1)
behav_final_redcap$aud_group <- factor(behav_final_redcap$aud_group, levels = c("AUD", "HC"))
contrasts(behav_final_redcap$aud_group) <- abs(contr.treatment(2)-1)

contrasts(behav_final$outcome_pred) <- contr.treatment(2)
contrasts(behav_final_redcap$outcome_pred) <- contr.treatment(2)

# se function
se <- function(x) sd(x, na.rm=TRUE)/sqrt(length(x)-sum(is.nan(x)))

# number notation without exponentials
options(scipen = 50)
```

# Pleasantness and craving rating

## Prepare dfs

```{r}
# get df with taste and craving ratings per subject and block
behav_rating <- behav_final %>%
  group_by(ID,reinforcer_type) %>%
  select(ID,reinforcer_type,ID_block,taste1, taste2, crave1, crave2) %>%
  distinct() %>%
  mutate(taste_diff=taste2-taste1,
         crave_diff=crave2-crave1)
behav_rating <- merge(behav_rating,redcap,by="ID",all.x = T) # merge with demographic data for linear mixed-effects regression

behav_rating <- behav_rating %>%
  mutate(taste_mean = ((taste1 + taste2)/2),
         crave_mean = ((crave1 + crave2)/2))

# create long dfs
behav_rating_long <- behav_rating %>%
  select(ID, aud_group, aud_sum, MRI_audit_sum, reinforcer_type, taste1, taste2, crave1, crave2) %>%
  pivot_longer(cols = c(taste1, taste2, crave1, crave2), names_to = "ratings")

behav_rating_long_taste <- behav_rating_long %>%
  filter(ratings %in% c("taste1", "taste2"))

behav_rating_long_crave <- behav_rating_long %>%
  filter(ratings %in% c("crave1", "crave2"))

behav_rating_long_taste$ratings <- factor(behav_rating_long_taste$ratings)
contrasts(behav_rating_long_taste$ratings) <- contr.treatment(2)

behav_rating_long_crave$ratings <- factor(behav_rating_long_crave$ratings)
contrasts(behav_rating_long_crave$ratings) <- contr.treatment(2)

# create wide df containing demo data and taste and crave fmri covariates
behav_rating_wide <- behav_final_redcap %>%
  select(ID, reinforcer_type, taste1, taste2, crave1, crave2) %>%
  mutate(taste_diff = taste2-taste1,
         crave_diff = crave2-crave1) %>%
  distinct() %>%
  pivot_wider(names_from = reinforcer_type, values_from = c(taste1, taste2, taste_diff, crave1, crave2, crave_diff)) %>%
  rowwise() %>%
  mutate(taste_A = (taste1_A + taste2_A)/2,
         taste_J = (taste1_J + taste2_J)/2,
         crave_A = (crave1_A + crave2_A)/2,
         crave_J = (crave1_J + crave2_J)/2) %>%
  mutate(taste_AJ_diff = taste_A - taste_J,
         crave_AJ_diff = crave_A - crave_J) %>%
  mutate(taste_AJ = (taste_A + taste_J)/2,
         crave_AJ = (crave_A + crave_J)/2)

demo_rating_wide <- left_join(redcap, behav_rating_wide) %>%
  select(BA_smoking_days, age, taste_AJ_diff, crave_AJ_diff, BA_drinks_past3months, MRI_audit_sum, BA_drinks_weekday)

demo_rating_wide_aud <- left_join(redcap, behav_rating_wide) %>%
  filter(aud_group == "AUD") %>%
  select(BA_smoking_days, age, taste_AJ_diff, crave_AJ_diff, BA_drinks_past3months, MRI_audit_sum, BA_drinks_weekday)

demo_rating_wide_hc <- left_join(redcap, behav_rating_wide) %>%
  filter(aud_group == "HC") %>%
  select(BA_smoking_days, age, taste_AJ_diff, crave_AJ_diff, BA_drinks_past3months, MRI_audit_sum, BA_drinks_weekday)
```

## Descriptive stats

```{r}
d_rating_all<- behav_rating %>%
  dplyr::summarise(across(c('taste1','taste2','crave1','crave2','taste_diff','crave_diff', 'taste_mean', 'crave_mean'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

d_rating <- behav_rating %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('taste1','taste2','crave1','crave2','taste_diff','crave_diff', 'taste_mean', 'crave_mean'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

d_rating_nan <- behav_rating %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('taste1','taste2','crave1','crave2','taste_diff','crave_diff','taste_mean','crave_mean'), 
                          .fns=list('_na' = ~sum(is.na(.)))))
d_rating_nan

# alc AUD
stats <- d_rating[1,-1:-2] %>% gather(stat, val) %>%
  separate(stat, into = c("var", "stat"), sep = "__") %>%
  spread(stat, val) %>%
  mutate(across(c('max','mean','min','sd'), round, 2))
stats

# alc HC
stats <- d_rating[2,-1:-2] %>% gather(stat, val) %>%
  separate(stat, into = c("var", "stat"), sep = "__") %>%
  spread(stat, val) %>%
  mutate(across(c('max','mean','min','sd'), round, 2))
stats

# jui AUD
stats <- d_rating[3,-1:-2] %>% gather(stat, val) %>%
  separate(stat, into = c("var", "stat"), sep = "__") %>%
  spread(stat, val) %>%
  mutate(across(c('max','mean','min','sd'), round, 2))
stats

# jui HC
stats <- d_rating[4,-1:-2] %>% gather(stat, val) %>%
  separate(stat, into = c("var", "stat"), sep = "__") %>%
  spread(stat, val) %>%
  mutate(across(c('max','mean','min','sd'), round, 2))
stats
```

## Linear mixed-effects regression

### Taste ratings 

#### AUD group

```{r}
m_taste_time <- lmer(value ~ 1 + reinforcer_type*aud_group*ratings + (1|ID), 
                     data=behav_rating_long_taste,
                     control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_taste_time,
          dv.labels=c("m_taste_time"), digits=3, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))#

check_model(m_taste_time, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq") )
```

```{r}
m_taste <- lmer(value ~ 1 + reinforcer_type*aud_group + (1 | ID), 
                     data=behav_rating_long_taste,
                     control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_taste,
          dv.labels=c("m_taste"), digits=3, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_taste, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq") )
```

```{r}
emmeans(m_taste, specs = pairwise ~ reinforcer_type|aud_group, lmer.df = "satterthwaite")
emmeans(m_taste, specs = pairwise ~ aud_group|reinforcer_type, lmer.df = "satterthwaite")
```

```{r}
plot_model(m_taste, type = "pred", terms = c("aud_group", "reinforcer_type"))
```


#### AUDIT criteria

```{r}
m_taste_time_audit <- lmer(value ~ 1 + reinforcer_type*MRI_audit_sum*ratings + (1|ID), 
                     data=behav_rating_long_taste,
                     control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_taste_time_audit,
          dv.labels=c("m_taste_time"), digits=3, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_taste_time_audit, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq") )
```

```{r}
m_taste_audit <- lmer(value ~ 1 + reinforcer_type*MRI_audit_sum + (1|ID), 
                     data=behav_rating_long_taste,
                     control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_taste_audit,
          dv.labels=c("m_taste"), digits=3, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_taste_audit, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq") )
```

```{r}
summary(emtrends(m_taste_audit, "reinforcer_type", var = "MRI_audit_sum", lmer.df = "satterthwaite"), infer=TRUE)
```

### Craving ratings 

#### AUD group

```{r}
m_crave_time <- lmer(value ~ 1 + reinforcer_type*aud_group*ratings + (1|ID), 
                     data=behav_rating_long_crave,
                     control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_crave_time,
          dv.labels=c("m_crave_time"), digits=3, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_crave_time, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq") )
```

```{r}
emmeans(m_crave_time, specs = pairwise ~ reinforcer_type|aud_group|ratings, lmer.df = "satterthwaite")

emmeans(m_crave_time, specs = pairwise ~ aud_group|reinforcer_type|ratings, lmer.df = "satterthwaite")
```

```{r}
plot_model(m_crave_time, type = "pred", terms = c("reinforcer_type", "aud_group"))
```

```{r}
m_crave <- lmer(value ~ 1 + reinforcer_type*aud_group + (1|ID), 
                     data=behav_rating_long_crave,
                     control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_crave,
          dv.labels=c("m_crave_time"), digits=3, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_crave, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq") )
```

```{r}
emmeans(m_crave, specs = pairwise ~ reinforcer_type|aud_group, lmer.df = "satterthwaite")

emmeans(m_crave, specs = pairwise ~ aud_group|reinforcer_type, lmer.df = "satterthwaite")
```

#### AUDIT criteria

```{r}
m_crave_time_audit <- lmer(value ~ 1 + reinforcer_type*MRI_audit_sum*ratings + (1|ID), 
                     data=behav_rating_long_crave,
                     control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_crave_time_audit,
          dv.labels=c("m_crave_time"), digits=3, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_crave_time_audit, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))
```

```{r}
summary(emtrends(m_crave_time_audit, c("reinforcer_type", "ratings"), var = "MRI_audit_sum", lmer.df = "satterthwaite"), infer=TRUE)
```

```{r}
plot_model(m_crave_time_audit, type = "pred", terms = c("MRI_audit_sum", "ratings", "reinforcer_type"))
```

```{r}
m_crave_audit <- lmer(value ~ 1 + reinforcer_type*MRI_audit_sum + (1|ID), 
                     data=behav_rating_long_crave,
                     control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_crave_audit,
          dv.labels=c("m_crave_time"), digits=3, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_crave_audit, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))
```

```{r}
summary(emtrends(m_crave_audit, "reinforcer_type", var = "MRI_audit_sum"), infer=TRUE)
```

## Plotting

### Taste per time point, group, reinforcer type

```{r}
fig_taste <- ggplot(behav_rating_long_taste, aes(x = ratings, y = value, fill = reinforcer_type)) +
  geom_violin() +
  geom_boxplot(aes(group=interaction(ratings,reinforcer_type)), 
               width=0.1, position=position_dodge(width = 0.9),
               size=0.8) + 
  facet_wrap(~aud_group, scales="fixed") +
  scale_x_discrete("Timepoint", labels=c('pre', 'post')) +
  scale_y_continuous("Taste rating") +
  theme_light(base_size=18) +
  theme(legend.position = "top") +
  scale_fill_brewer(name="Reinforcer type", 
                    labels=c("alcohol", "juice"),
                    palette = "Accent")

fig_taste
```

### Craving per time point, group, reinforcer type

```{r}
fig_crave <- ggplot(behav_rating_long_crave, aes(x = ratings, y = value, fill = reinforcer_type)) +
  geom_violin() +
  geom_boxplot(aes(group=interaction(ratings,reinforcer_type)), 
               width=0.1, position=position_dodge(width = 0.9),
               size=0.8) + 
  facet_wrap(~aud_group, scales="fixed") +
  scale_x_discrete("Timepoint", labels=c('pre', 'post')) +
  scale_y_continuous("Craving rating") +
  theme_light(base_size=18) +
  theme(legend.position = "top") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent")

fig_crave
```

```{r}
# save combined plot
fig_taste_crave <- ggarrange(fig_taste, fig_crave,
          labels = c("A", "B"),
          ncol = 2, nrow = 1,
          common.legend = TRUE, legend="bottom")
fig_taste_crave

png(file.path(project_path, "Manuscript/Figures", paste("taste_crave_", sample, ".png", sep="")), width = 24, height = 10, units='cm', res = 600)
fig_taste_crave
dev.off()
```

## Association taste and craving ratings with psychometric characteristics within AUD group + VIF

```{r}
# all
chart.Correlation(demo_rating_wide, histogram=T, pch=1)

model_aud <- lm(BA_drinks_weekday ~ BA_smoking_days + age + crave_AJ_diff + MRI_audit_sum + BA_drinks_past3months, data=demo_rating_wide)

vif(model_aud)

# AUD
chart.Correlation(demo_rating_wide_aud, histogram=T, pch=1)

model_aud <- lm(BA_drinks_weekday ~ BA_smoking_days + age + taste_AJ_diff + crave_AJ_diff + MRI_audit_sum, data=demo_rating_wide_aud)

vif(model_aud)

# HC
chart.Correlation(demo_rating_wide_hc, histogram=T, pch=1)

model_hc <- lm(BA_drinks_weekday ~ BA_smoking_days + age + taste_AJ_diff + crave_AJ_diff + MRI_audit_sum + BA_drinks_past3months, data=demo_rating_wide_hc)

vif(model_hc)
```

# Correct choices

## Prepare dfs

```{r}
# get p correct per subject and block for linear mixed-effects regression
df_c <- behav_final %>%
  group_by(ID,reinforcer_type) %>%
  summarise_at(vars(correct), list(p_correct = mean), na.rm=T)

df_c_rating <- merge(df_c,behav_rating,by=c("ID","reinforcer_type")) # merge with demographic data for linear mixed-effects regression

df_c <- merge(df_c,redcap,by="ID") # merge with demographic data for linear mixed-effects regression

# get p correct per block and aud group and trial for plotting
df_c_block_trial_group <- behav_final_redcap %>%
  group_by(aud_group,reinforcer_type,trial_block) %>%
  dplyr::summarise(p_correct = mean(correct, na.rm = TRUE),
            ci_l = ci(correct, na.rm=TRUE)[2],
            ci_u = ci(correct, na.rm=TRUE)[3]
  )
```

## Descriptive stats

```{r}
# per group and reinforcer type
df_c_stats <- behav_final_redcap %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('correct'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))
df_c_stats

df_c_stats_nan <- behav_final_redcap %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('correct'), .fns=
                   list('_na' = ~sum(is.na(.)))))
df_c_stats_nan

# per group
df_c_stats <- behav_final_redcap %>%
  group_by(aud_group) %>%
  dplyr::summarise(across(c('correct'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

df_c_stats

df_c_stats_nan <- behav_final_redcap %>%
  group_by(aud_group) %>%
  dplyr::summarise(across(c('correct'), .fns=
                   list('_na' = ~sum(is.na(.)))))

df_c_stats_nan

# per reinforcer type
df_c_stats <- behav_final_redcap %>%
  group_by(reinforcer_type) %>%
  dplyr::summarise(across(c('correct'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

df_c_stats

df_c_stats_nan <- behav_final_redcap %>%
  group_by(reinforcer_type) %>%
  dplyr::summarise(across(c('correct'), .fns=
                   list('_na' = ~sum(is.na(.)))))

df_c_stats_nan

# overall
df_c_stats <- behav_final_redcap %>%
  dplyr::summarise(across(c('correct'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

df_c_stats

df_c_stats_nan <- behav_final_redcap %>%
  dplyr::summarise(across(c('correct'), .fns=
                   list('_na' = ~sum(is.na(.)))))

df_c_stats_nan
```

## AUD group

```{r}
m_correct_time_1 <- glmer(correct ~ 1 + reinforcer_type*aud_group*trial_block + (1 + reinforcer_type + trial_block | ID), 
                         data=behav_final_redcap, 
                         family = binomial, 
                         control=glmerControl(calc.derivs=FALSE))

tab_model(m_correct_time_1,
          dv.labels=c("m_correct_log"), digits=3, digits.re=2, show.est = T, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_correct_time_1, check=c("pp_check", "reqq", "qq"))
```

```{r}
m_correct_1 <- glmer(correct ~ 1 + reinforcer_type*aud_group + (1 + reinforcer_type | ID), 
                         data=behav_final_redcap, 
                         family = binomial, 
                         control=glmerControl(calc.derivs=FALSE))

tab_model(m_correct_1,
          dv.labels=c("m_correct_log"), digits=3, digits.re=2, show.est = T, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_correct_1, check=c("pp_check", "reqq", "qq"))
```

##### Controlled for taste


## AUDIT criteria

```{r}
m_correct_time_1_auditsum <- glmer(correct ~ 1 + reinforcer_type*MRI_audit_sum*trial_block + (1 + reinforcer_type + trial_block | ID), 
                                  data=behav_final_redcap, 
                                  family = binomial, 
                                  control=glmerControl(calc.derivs=FALSE))

tab_model(m_correct_time_1_auditsum,
          dv.labels=c("m_correct_log"), digits=3, digits.re=2, transform = NULL, show.est = T, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_correct_time_1_auditsum, check=c("pp_check", "reqq", "qq"))
```

```{r}
m_correct_1_auditsum <- glmer(correct ~ 1 + reinforcer_type*MRI_audit_sum + (1 + reinforcer_type | ID), 
                                  data=behav_final_redcap, 
                                  family = binomial, 
                                  control=glmerControl(calc.derivs=FALSE))

tab_model(m_correct_1_auditsum,
          dv.labels=c("m_correct_log"), digits=3, digits.re=2, transform = NULL, show.est = T, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_correct_1_auditsum, check=c("pp_check", "reqq", "qq"))
```

## Plotting

### Per group and reinforcer type

```{r}
fig_correct <- ggplot(df_c, aes(reinforcer_type, y = p_correct*100, fill=reinforcer_type)) +
  geom_violin() +
  geom_boxplot(width=0.1, size=0.8) + 
  facet_wrap(~aud_group, scales="fixed") +
  scale_y_continuous("% Correct choices", limits = c(0,100)) +
  theme_light(base_size=18) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        legend.position = "bottom") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent")
fig_correct
```

### Correct choices over course of task

```{r}
fig_correct_time <- ggplot(df_c_block_trial_group, aes(x=trial_block, y=p_correct*100, group=reinforcer_type)) +
  geom_line(aes(color=reinforcer_type), linewidth=0.8) +
  geom_ribbon(aes(ymin = ci_l*100, ymax = ci_u*100, fill = reinforcer_type), alpha = 0.2) + 
  facet_wrap(~aud_group, scales="free_y") +
  scale_y_continuous("% Correct choices", limits = c(-5,105)) +
  scale_x_continuous(NULL) +
  theme_light(base_size=18) +
  theme(legend.position = "right") +
  scale_color_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent")

fig_correct_time

```

# Association correct choices & ratings

## Linear mixed-effects regression taste rating

```{r}
m_c_taste1=lmer(p_correct~taste1 + (1 | ID),
                data=df_c_rating,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_c_taste1,
          dv.labels=c("m_c_taste1"), digits=3, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_c_taste1, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

# robust estimation
m_c_taste1_robust=rlmer(p_correct~taste1 + (1 | ID),
                data=df_c_rating,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_c_taste1_robust,
          dv.labels=c("m_c_taste1"), digits=3, digits.re=2, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,
          CSS = css_theme("cells"))

plot(m_c_taste1_robust)
```

```{r}
m_c_taste2=lmer(p_correct~taste2 + (1 | ID),
                data=df_c_rating,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_c_taste2,
          dv.labels=c("m_c_taste2"), digits=3, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_c_taste2, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

# robust estimation
m_c_taste2_robust=rlmer(p_correct~taste2 + (1 | ID),
                data=df_c_rating,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_c_taste2_robust,
          dv.labels=c("m_c_taste2"), digits=3, digits.re=2, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,
          CSS = css_theme("cells"))

plot(m_c_taste2_robust)
```

```{r}
m_c_taste_diff=lmer(p_correct~taste_diff + (1 | ID),
                data=df_c_rating,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_c_taste_diff,
          dv.labels=c("m_c_taste_diff"), digits=3, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_c_taste_diff, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

# robust estimation
m_c_taste_diff_robust=rlmer(p_correct~taste_diff + (1 | ID),
                data=df_c_rating,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_c_taste_diff_robust,
          dv.labels=c("m_c_taste_diff"), digits=3, digits.re=2, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,
          CSS = css_theme("cells"))

plot(m_c_taste_diff_robust)
```

## Linear mixed-effects regression craving rating

```{r}
m_c_crave1=lmer(p_correct~crave1 + (1 | ID),
                data=df_c_rating,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_c_crave1,
          dv.labels=c("m_c_crave1"), digits=3, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_c_crave1, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

# robust estimation
m_c_crave1_robust=rlmer(p_correct~crave1 + (1 | ID),
                data=df_c_rating,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_c_crave1_robust,
          dv.labels=c("m_c_crave1"), digits=3, digits.re=2, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,
          CSS = css_theme("cells"))

plot(m_c_crave1_robust)
```

```{r}
m_c_crave2=lmer(p_correct~crave2 + (1 | ID),
                data=df_c_rating,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_c_crave2,
          dv.labels=c("m_c_crave2"), digits=3, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_c_crave2, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

# robust estimation
m_c_crave2_robust=rlmer(p_correct~crave2 + (1 | ID),
                data=df_c_rating,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_c_crave2_robust,
          dv.labels=c("m_c_crave2"), digits=3, digits.re=2, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,
          CSS = css_theme("cells"))

plot(m_c_crave2_robust)
```

```{r}
m_c_crave_diff=lmer(p_correct~crave_diff + (1 | ID),
                data=df_c_rating,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_c_crave_diff,
          dv.labels=c("m_c_crave_diff"), digits=3, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_c_crave_diff, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

# robust estimation
m_c_crave_diff_robust=rlmer(p_correct~crave_diff + (1 | ID),
                data=df_c_rating,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_c_crave_diff_robust,
          dv.labels=c("m_c_crave_diff"), digits=3, digits.re=2, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,
          CSS = css_theme("cells"))

plot(m_c_crave_diff_robust)
```

# Win-Stay behavior: Repeating the same action that was rewarded in previous trial

## Prepare dfs

```{r}
# get p correct per subject and block for linear mixed-effects regression
df_win_stay <- behav_final %>%
  group_by(ID,reinforcer_type,na.rm=T) %>%
  summarise_at(vars(stay,win_stay), list(p = mean), na.rm=T) %>%
  na.omit()
df_win_stay <- merge(df_win_stay,redcap,by="ID") # merge with demographic data for linear mixed-effects 

# get p correct per block and aud group and trial for plotting
df_win_stay_trial_group <- behav_final_redcap %>%
  group_by(aud_group,reinforcer_type,trial_block) %>%
  dplyr::summarise(p = mean(win_stay, na.rm = TRUE),
            ci_l = ci(win_stay, na.rm=TRUE)[2],
            ci_u = ci(win_stay, na.rm=TRUE)[3]
  )
```

## Descriptive stats

```{r}
# per group and reinforcer type
df_win_stay_stats <- behav_final_redcap %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('win_stay'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))
df_win_stay_stats

df_win_stay_stats_nan <- behav_final_redcap %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('win_stay'), .fns=
                   list('_na' = ~sum(is.na(.)))))
df_win_stay_stats_nan

# per group
df_win_stay_stats <- behav_final_redcap %>%
  group_by(aud_group) %>%
  dplyr::summarise(across(c('win_stay'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

df_win_stay_stats

df_win_stay_stats_nan <- behav_final_redcap %>%
  group_by(aud_group) %>%
  dplyr::summarise(across(c('win_stay'), .fns=
                   list('_na' = ~sum(is.na(.)))))

df_win_stay_stats_nan

# per reinforcer type
df_win_stay_stats <- behav_final_redcap %>%
  group_by(reinforcer_type) %>%
  dplyr::summarise(across(c('win_stay'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

df_win_stay_stats

df_win_stay_stats_nan <- behav_final_redcap %>%
  group_by(reinforcer_type) %>%
  dplyr::summarise(across(c('win_stay'), .fns=
                   list('_na' = ~sum(is.na(.)))))

df_win_stay_stats_nan

# overall
df_win_stay_stats <- behav_final_redcap %>%
  dplyr::summarise(across(c('win_stay'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

df_win_stay_stats

df_win_stay_stats_nan <- behav_final_redcap %>%
  dplyr::summarise(across(c('win_stay'), .fns=
                   list('_na' = ~sum(is.na(.)))))

df_win_stay_stats_nan
```

## AUD group

```{r}
m_win_stay_time_1=glmer(win_stay~reinforcer_type*aud_group*trial_block + (1 + reinforcer_type + trial_block | ID),
                data=behav_final_redcap,
                family=binomial,
                control=glmerControl(calc.derivs=FALSE))

tab_model(m_win_stay_time_1,
          dv.labels=c("m_stay"), digits=3, digits.re=2, show.est = T, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_win_stay_time_1, check=c("pp_check", "reqq", "qq"))
```

```{r}
m_win_stay_1=glmer(win_stay~reinforcer_type*aud_group + (1 + reinforcer_type | ID),
                data=behav_final_redcap,
                family=binomial,
                control=glmerControl(calc.derivs=FALSE))

tab_model(m_win_stay_1,
          dv.labels=c("m_stay"), digits=3, digits.re=2, show.est = T, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_win_stay_1, check=c("pp_check", "reqq", "qq"))
```

## AUDIT criteria

```{r}
m_win_stay_time_1_auditsum=glmer(win_stay~reinforcer_type*MRI_audit_sum*trial_block + (1 + reinforcer_type + trial_block | ID),
                data=behav_final_redcap,
                family=binomial,
                control=glmerControl(calc.derivs=FALSE))

tab_model(m_win_stay_time_1_auditsum,
          dv.labels=c("m_stay"), digits=3, digits.re=2, transform = NULL, show.est = T, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_win_stay_time_1_auditsum, check=c("pp_check", "reqq", "qq"))
```

```{r}
m_win_stay_1_auditsum=glmer(win_stay~reinforcer_type*MRI_audit_sum + (1 + reinforcer_type | ID),
                data=behav_final_redcap,
                family=binomial,
                control=glmerControl(calc.derivs=FALSE))

tab_model(m_win_stay_1_auditsum,
          dv.labels=c("m_stay"), digits=3, digits.re=2, transform = NULL, show.est = T, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_win_stay_1_auditsum, check=c("pp_check", "reqq", "qq"))
```

## Plotting

### Violin plot per aud group and reinforcer type

```{r}
fig_win_stay <- ggplot(df_win_stay, aes(reinforcer_type, y = win_stay_p*100, fill=reinforcer_type)) +
  geom_violin() +
  geom_boxplot(width=0.1, size=0.8) + 
  facet_wrap(~ aud_group, scales="fixed") +
  scale_y_continuous("% Win-stay", limits = c(0,100)) +
  theme_light(base_size=18) +
  theme(axis.title.x=element_blank(),
      axis.text.x=element_blank(),
      axis.ticks.x=element_blank(),
      legend.position = "bottom") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent")

fig_win_stay
```

### Win-stay behavior over course of task

```{r}
fig_winstay_time <- ggplot(df_win_stay_trial_group, aes(x=trial_block, y=p*100, group=reinforcer_type)) +
  geom_line(aes(color=reinforcer_type), linewidth=0.8) +
  geom_ribbon(aes(ymin = ci_l*100, ymax = ci_u*100, fill = reinforcer_type), alpha = 0.2) + 
  facet_wrap(~aud_group, scales="free_y") +
  scale_y_continuous("% Win-stay", limits = c(-5,105)) +
  scale_x_continuous(NULL) +
  theme_light(base_size=18) +
  theme(legend.position = "right") +
  scale_color_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent")

fig_winstay_time

```

# No-Win-Switch behavior: Switching the action if it was not rewarded in previous trial

## Prepare dfs

```{r}
# get p correct per subject and block for linear mixed-effects regression
df_nowin_switch <- behav_final %>%
  group_by(ID,reinforcer_type,na.rm=T) %>%
  summarise_at(vars(stay,nowin_switch), list(p = mean), na.rm=T) %>%
  na.omit()
df_nowin_switch <- merge(df_nowin_switch,redcap,by="ID") # merge with demographic data for linear mixed-effects 

# get p correct per block and aud group and trial for plotting
df_nowin_switch_trial_group <- behav_final_redcap %>%
  group_by(aud_group,reinforcer_type,trial_block) %>%
  dplyr::summarise(p = mean(nowin_switch, na.rm = TRUE),
            ci_l = ci(nowin_switch, na.rm=TRUE)[2],
            ci_u = ci(nowin_switch, na.rm=TRUE)[3]
  )
```

## Descriptive stats

```{r}
# per group and reinforcer type
df_nowin_switch_stats <- behav_final_redcap %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('nowin_switch'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))
df_nowin_switch_stats

df_nowin_switch_stats_nan <- behav_final_redcap %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('nowin_switch'), .fns=
                   list('_na' = ~sum(is.na(.)))))
df_nowin_switch_stats_nan

# per group
df_nowin_switch_stats <- behav_final_redcap %>%
  group_by(aud_group) %>%
  dplyr::summarise(across(c('nowin_switch'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

df_nowin_switch_stats

df_nowin_switch_stats_nan <- behav_final_redcap %>%
  group_by(aud_group) %>%
  dplyr::summarise(across(c('nowin_switch'), .fns=
                   list('_na' = ~sum(is.na(.)))))

df_nowin_switch_stats_nan

# per reinforcer type
df_nowin_switch_stats <- behav_final_redcap %>%
  group_by(reinforcer_type) %>%
  dplyr::summarise(across(c('nowin_switch'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

df_nowin_switch_stats

df_nowin_switch_stats_nan <- behav_final_redcap %>%
  group_by(reinforcer_type) %>%
  dplyr::summarise(across(c('nowin_switch'), .fns=
                   list('_na' = ~sum(is.na(.)))))

df_nowin_switch_stats_nan

# overall
df_nowin_switch_stats <- behav_final_redcap %>%
  dplyr::summarise(across(c('nowin_switch'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

df_nowin_switch_stats

df_nowin_switch_stats_nan <- behav_final_redcap %>%
  dplyr::summarise(across(c('nowin_switch'), .fns=
                   list('_na' = ~sum(is.na(.)))))

df_nowin_switch_stats_nan
```

## AUD group

```{r}
m_nowin_switch_time_1=glmer(nowin_switch~reinforcer_type*aud_group*trial_block + (1 + reinforcer_type + trial_block | ID),
                data=behav_final_redcap,
                family=binomial,
                control=glmerControl(calc.derivs=FALSE))

tab_model(m_nowin_switch_time_1,
          dv.labels=c("m_switch"), digits=3, digits.re=2, show.est = T, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_nowin_switch_time_1, check=c("pp_check", "reqq", "qq"))
```

```{r}
m_nowin_switch_1=glmer(nowin_switch~reinforcer_type*aud_group + (1 + reinforcer_type | ID),
                data=behav_final_redcap,
                family=binomial,
                control=glmerControl(calc.derivs=FALSE))

tab_model(m_nowin_switch_1,
          dv.labels=c("m_switch"), digits=3, digits.re=2, show.est = T, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_nowin_switch_1, check=c("pp_check", "reqq", "qq"))
```

## AUDIT criteria

```{r}
m_nowin_switch_time_1_auditsum=glmer(nowin_switch~reinforcer_type*MRI_audit_sum*trial_block + (1 + reinforcer_type + trial_block | ID),
                data=behav_final_redcap,
                family=binomial,
                control=glmerControl(calc.derivs=FALSE))

tab_model(m_nowin_switch_time_1_auditsum,
          dv.labels=c("m_switch"), digits=3, digits.re=2, transform = NULL, show.est = T, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_nowin_switch_time_1_auditsum, check=c("pp_check", "reqq", "qq"))
```

```{r}
m_nowin_switch_1_auditsum=glmer(nowin_switch~reinforcer_type*MRI_audit_sum + (1 + reinforcer_type | ID),
                data=behav_final_redcap,
                family=binomial,
                control=glmerControl(calc.derivs=FALSE))

tab_model(m_nowin_switch_1_auditsum,
          dv.labels=c("m_switch"), digits=3, digits.re=2, transform = NULL, show.est = T, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_nowin_switch_1_auditsum, check=c("pp_check", "reqq", "qq"))
```

## Plotting

### Violin plot per aud group and reinforcer type

```{r}

fig_nowin_switch <- ggplot(df_nowin_switch, aes(reinforcer_type, y = nowin_switch_p*100, fill=reinforcer_type)) +
  geom_violin() +
  geom_boxplot(width=0.1, size=0.8) + 
  facet_wrap(~ aud_group, scales="fixed") +
  scale_y_continuous("% No-win-switch", limits = c(0,100)) +
  theme_light(base_size=18) +
  theme(axis.title.x=element_blank(),
      axis.text.x=element_blank(),
      axis.ticks.x=element_blank(),
      legend.position = "bottom") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent")

fig_nowin_switch

```

### No-win_switch behavior over course of task

```{r}
fig_nowinswitch_time <- ggplot(df_nowin_switch_trial_group, aes(x=trial_block, y=p*100, group=reinforcer_type)) +
  geom_line(aes(color=reinforcer_type), linewidth=0.8) +
  geom_ribbon(aes(ymin = ci_l*100, ymax = ci_u*100, fill = reinforcer_type), alpha = 0.2) + 
  facet_wrap(~aud_group, scales="free_y") +
  scale_y_continuous("% No-win-switch", limits = c(-5,105)) +
  scale_x_continuous(NULL) +
  theme_light(base_size=18) +
  theme(legend.position = "right") +
  scale_color_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent") +
    scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent")

fig_nowinswitch_time

```

# Reaction times

## Prepare dfs

```{r}
# get rt per subject and block for linear mixed-effects regression
df_rt <- behav_final %>%
  group_by(ID,reinforcer_type) %>%
  summarise_at(vars(rt), list(p = mean)) %>%
  na.omit()
df_rt <- merge(df_rt,redcap,by="ID") # merge with demographic data for linear mixed-effects 

# get p correct per block and aud group and trial for plotting
df_rt_trial_group <- behav_final_redcap %>%
  group_by(aud_group,reinforcer_type,trial_block) %>%
  dplyr::summarise(p = mean(rt, na.rm = TRUE),
            ci_l = ci(rt, na.rm=TRUE)[2],
            ci_u = ci(rt, na.rm=TRUE)[3]
  )

```

## Descriptive stats

```{r}
# per group and reinforcer type
df_rt_stats <- behav_final_redcap %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('rt'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))
df_rt_stats

df_rt_stats_nan <- behav_final_redcap %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('rt'), .fns=
                   list('_na' = ~sum(is.na(.)))))
df_rt_stats_nan

# per group
df_rt_stats <- behav_final_redcap %>%
  group_by(aud_group) %>%
  dplyr::summarise(across(c('rt'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

df_rt_stats

df_rt_stats_nan <- behav_final_redcap %>%
  group_by(aud_group) %>%
  dplyr::summarise(across(c('rt'), .fns=
                   list('_na' = ~sum(is.na(.)))))

df_rt_stats_nan

# per reinforcer type
df_rt_stats <- behav_final_redcap %>%
  group_by(reinforcer_type) %>%
  dplyr::summarise(across(c('rt'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

df_rt_stats

df_rt_stats_nan <- behav_final_redcap %>%
  group_by(reinforcer_type) %>%
  dplyr::summarise(across(c('rt'), .fns=
                   list('_na' = ~sum(is.na(.)))))

df_rt_stats_nan

# overall
df_rt_stats <- behav_final_redcap %>%
  dplyr::summarise(across(c('rt'), .fns=
                   list('_mean' = mean,
                        '_sd' = sd,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

df_rt_stats

df_rt_stats_nan <- behav_final_redcap %>%
  dplyr::summarise(across(c('rt'), .fns=
                   list('_na' = ~sum(is.na(.)))))

df_rt_stats_nan
```

## AUD group

```{r}
m_rt_trial_1=lmer(rt~reinforcer_type*aud_group*trial_block + (1 + reinforcer_type + trial_block | ID),
                data=behav_final_redcap,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_rt_trial_1,
          dv.labels=c("m_rt_trial"), digits=3, digits.re=2, transform = NULL, show.est = T, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_rt_trial_1, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

# robust estimation
m_rt_trial_1_robust=rlmer(rt~reinforcer_type*aud_group*trial_block + (1 + reinforcer_type + trial_block | ID),
                data=behav_final_redcap,
                control=lmerControl(calc.derivs=FALSE))

plot(m_rt_trial_1_robust)
```

Derive p-values for robust model according to https://stats.stackexchange.com/questions/430490/obtaining-p-values-in-a-robustlmm-mixed-model-via-satterthwaite-approximated-dfs

```{r}
# get Satterthwaite DFs from non-robust model
coefs <- data.frame(coef(summary(m_rt_trial_1)))

# get coefficients from robust model to extract t-values
coefs.robust <- coef(summary(m_rt_trial_1_robust))

# calculate p-values based on robust t-values and non-robust approx. DFs
p.values <- 2*pt(abs(coefs.robust[,3]), coefs$df, lower=FALSE)
as.data.frame(p.values)
```

```{r}
summary(emtrends(m_rt_trial_1, c("reinforcer_type"), var = "trial_block", lmer.df = "satterthwaite", lmerTest.limit = 5702), infer=TRUE)

summary(emtrends(m_rt_trial_1, c("reinforcer_type", "aud_group"), var = "trial_block", lmer.df = "satterthwaite", lmerTest.limit = 5702), infer=TRUE)
pairs(emtrends(m_rt_trial_1, c("reinforcer_type", "aud_group"), var = "trial_block", lmer.df = "satterthwaite", lmerTest.limit = 5702))
```

```{r}
plot_model(m_rt_trial_1, type = "pred", terms = c("trial_block [all]", "reinforcer_type", "aud_group")) +
  theme_light(base_size = 14)
```

```{r}
m_rt_1=lmer(p~reinforcer_type*aud_group + (1 | ID),
                data=df_rt,
                control=lmerControl(calc.derivs=FALSE),
                REML=F)

tab_model(m_rt_1,
          dv.labels=c("m_rt"), digits=3, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_rt_1, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

# robust estimation
m_rt_1_robust=rlmer(p~reinforcer_type*aud_group + (1 | ID),
                data=df_rt,
                control=lmerControl(calc.derivs=FALSE),
                REML=F)

plot(m_rt_1_robust)
```

Derive p-values for robust model according to https://stats.stackexchange.com/questions/430490/obtaining-p-values-in-a-robustlmm-mixed-model-via-satterthwaite-approximated-dfs

```{r}
# get Satterthwaite DFs from non-robust model
coefs <- data.frame(coef(summary(m_rt_1)))

# get coefficients from robust model to extract t-values
coefs.robust <- coef(summary(m_rt_1_robust))

# calculate p-values based on robust t-values and non-robust approx. DFs
p.values <- 2*pt(abs(coefs.robust[,3]), coefs$df, lower=FALSE)
as.data.frame(p.values)
```

## AUDIT criteria

```{r}
m_rt_trial_1_auditsum=lmer(rt~reinforcer_type*MRI_audit_sum*trial_block + (1 + reinforcer_type + trial_block | ID),
                data=behav_final_redcap,
                control=lmerControl(calc.derivs=FALSE))

tab_model(m_rt_trial_1_auditsum,
          dv.labels=c("m_rt_trial"), digits=3, digits.re=2, transform = NULL, show.est = T, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_rt_trial_1_auditsum, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

# robust estimation
m_rt_trial_1_auditsum_robust=rlmer(rt~reinforcer_type*MRI_audit_sum*trial_block + (1 + reinforcer_type + trial_block | ID),
                data=behav_final_redcap,
                control=lmerControl(calc.derivs=FALSE))

plot(m_rt_trial_1_auditsum_robust)
```

Derive p-values for robust model according to https://stats.stackexchange.com/questions/430490/obtaining-p-values-in-a-robustlmm-mixed-model-via-satterthwaite-approximated-dfs

```{r}
# get Satterthwaite DFs from non-robust model
coefs <- data.frame(coef(summary(m_rt_trial_1_auditsum)))

# get coefficients from robust model to extract t-values
coefs.robust <- coef(summary(m_rt_trial_1_auditsum_robust))

# calculate p-values based on robust t-values and non-robust approx. DFs
p.values <- 2*pt(abs(coefs.robust[,3]), coefs$df, lower=FALSE)
as.data.frame(p.values)
```

```{r}
summary(emtrends(m_rt_trial_1_auditsum, c("reinforcer_type"), var = "trial_block", pbkrtest.limit = 5603), infer=TRUE)

summary(emtrends(m_rt_trial_1_auditsum, c("reinforcer_type", "MRI_audit_sum"), var = c("trial_block"), at = list(MRI_audit_sum = c(2.1,9.4,16.7)), pbkrtest.limit = 5603), infer=TRUE)
pairs(emtrends(m_rt_trial_1_auditsum, c("reinforcer_type", "MRI_audit_sum"), var = c("trial_block"), at = list(MRI_audit_sum = c(2.1,9.4,16.7)), pbkrtest.limit = 5603))
```

```{r}
plot_model(m_rt_trial_1_auditsum, type = "pred", terms = c("trial_block [all]", "reinforcer_type", "MRI_audit_sum"))
```

```{r}
m_rt_1_auditsum=lmer(p~reinforcer_type*MRI_audit_sum + (1 | ID),
                data=df_rt,
                control=lmerControl(calc.derivs=FALSE),
                REML=F)

tab_model(m_rt_1_auditsum,
          dv.labels=c("m_rt"), digits=3, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci=FALSE,CSS = css_theme("cells"))

check_model(m_rt_1_auditsum, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

# robust estimation
m_rt_1_auditsum_robust=rlmer(p~reinforcer_type*MRI_audit_sum + (1 | ID),
                data=df_rt,
                control=lmerControl(calc.derivs=FALSE),
                REML=F)

plot(m_rt_1_auditsum_robust)
```

Derive p-values for robust model according to https://stats.stackexchange.com/questions/430490/obtaining-p-values-in-a-robustlmm-mixed-model-via-satterthwaite-approximated-dfs

```{r}
# get Satterthwaite DFs from non-robust model
coefs <- data.frame(coef(summary(m_rt_1_auditsum)))

# get coefficients from robust model to extract t-values
coefs.robust <- coef(summary(m_rt_1_auditsum_robust))

# calculate p-values based on robust t-values and non-robust approx. DFs
p.values <- 2*pt(abs(coefs.robust[,3]), coefs$df, lower=FALSE)
as.data.frame(p.values)
```

## Plotting

### Violin plot per aud group and reinforcer type

```{r}
fig_rt <- ggplot(df_rt, aes(reinforcer_type, y = p, fill=reinforcer_type)) +
  geom_violin() +
  geom_boxplot(width=0.1, size=0.8) + 
  facet_wrap(~ aud_group, scales="fixed") +
  scale_y_continuous("Reaction time (s)", limits = c(0,1)) +
  theme_light(base_size=18) +
  theme(axis.title.x=element_blank(),
      axis.text.x=element_blank(),
      axis.ticks.x=element_blank(),
      legend.position = "bottom") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent")

fig_rt
```

### RT over course of task

```{r}
fig_rt_time <- ggplot(df_rt_trial_group, aes(x=trial_block, y=p, group=reinforcer_type)) +
  geom_line(aes(color=reinforcer_type), linewidth=0.8) +
  geom_ribbon(aes(ymin = ci_l, ymax = ci_u, fill = reinforcer_type), alpha = 0.2) + 
  facet_wrap(~aud_group, scales="free_y") +
  scale_y_continuous("Reaction time (s)", limits = c(0,1)) +
  scale_x_continuous("Trial") +
  theme_light(base_size=18) +
  theme(legend.position = "right") +
  scale_color_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("alcohol", "juice"),
                  palette = "Accent")

fig_rt_time

```

# Save combined plots for publication

```{r}
# save combined plot
fig_correct_win_stay <- ggarrange(fig_correct, fig_win_stay, fig_nowin_switch, fig_rt,
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2,
          common.legend = TRUE, legend="bottom")
fig_correct_win_stay

png(file.path(project_path, "Manuscript/Figures", paste("correct_win_stay_", sample, ".png", sep="")), width = 16, height = 17, units='cm', res = 600)
fig_correct_win_stay
dev.off()
```

```{r}
# save combined plot
fig_correct_win_stay_rt_time <- ggarrange(fig_correct_time, fig_winstay_time, fig_nowinswitch_time, fig_rt_time,
          labels = c("A", "B", "C", "D"),
          ncol = 1, nrow = 4,
          common.legend = TRUE, legend="bottom")
fig_correct_win_stay_rt_time

png(file.path(project_path, "Manuscript/Figures", paste("correct_win_stay_time_", sample, ".png", sep="")), width = 16, height =28, units='cm', res = 600)
fig_correct_win_stay_rt_time
dev.off()
```
