---
title: "02_Behavioral_Analyses"
author: "Milena Musial"
format:
  html:
    embed-resources: true
    editor: visual
    toc: true
    toc-depth: 4
    number-sections: true
    number-depth: 4
editor_options: 
  chunk_output_type: inline
execute:
  warning: false
  message: false
---

# Preps

## General setup

```{r, echo=FALSE, results='hide'}

rm(list=ls())
#lapply(names(sessionInfo()$loadedOnly), require, character.only = TRUE)
#invisible(lapply(paste0('package:', names(sessionInfo()$otherPkgs)), detach, character.only=TRUE, unload=TRUE, force=TRUE))

# load packages
libs<-c("tidyverse", "stringr", "plyr", "dplyr", "lme4", "robustlmm", "lmerTest",
        "sjPlot", "ggpubr", "gmodels", "PerformanceAnalytics", "car", "performance",
        "emmeans", "psych", "confintROB")
invisible(sapply(libs, require, character.only=TRUE))

project_path <- "/Users/milenamusial/Library/CloudStorage/OneDrive-Charité-UniversitätsmedizinBerlin/PhD/04_B01/ILT"

# define sample
sample <- "n58" # n58, n56, n13

# load color
accent <- RColorBrewer::brewer.pal(7, "Accent")

if (sample == 'n58') {
  load(file.path(project_path, "WP2_ILT_DATA/Behav/behav_final_n58.RData"))
  load(file.path(project_path, "WP2_ILT_DATA/RedCap/redcap_n58_new.RData"))
  load(file.path(project_path, "WP2_ILT_DATA/Behav/behav_final_redcap_n58.RData"))
} else if (sample == 'n56') {
  load(file.path(project_path, "WP2_ILT_DATA/Behav/behav_final_n56.RData"))
  load(file.path(project_path, "WP2_ILT_DATA/RedCap/redcap_n56_new.RData"))
  load(file.path(project_path, "WP2_ILT_DATA/Behav/behav_final_redcap_n56.RData"))
} else if (sample == 'n13') {
  load(file.path(project_path, "WP2_ILT_DATA/RedCap/redcap_n71_new.RData"))
  redcap_new_71 <- redcap_new
  load(file.path(project_path, "WP2_ILT_DATA/RedCap/redcap_n58_new.RData"))
  redcap_new_58 <- redcap_new
  redcap_new <- redcap_new_71[! redcap_new_71$ID %in% redcap_new_58$ID, ]
  load(file.path(project_path, "WP2_ILT_DATA/Behav/behav_final_n71.RData"))
  behav_final <- behav_final[behav_final$ID %in% redcap_new$ID, ]
  load(file.path(project_path, "WP2_ILT_DATA/Behav/behav_final_redcap_n71.RData"))
  behav_final_redcap <- behav_final_redcap[behav_final_redcap$ID %in% redcap_new$ID, ]
  rm(list = c("redcap_new_58", "redcap_new_71"))
}

redcap <- redcap_new

##### Adapt basic dfs & set contrasts #####

behav_final <- behav_final %>%
  rowwise() %>%
  mutate(taste = (taste1+taste2)/2,
         crave = (crave1+crave2)/2,
         trial_block_centered = trial_block-1)

behav_final_redcap <- behav_final_redcap %>%
  rowwise() %>%
  mutate(taste = (taste1+taste2)/2,
         crave = (crave1+crave2)/2,
         trial_block_centered = trial_block-1)

# create outcome as predictor for stay switch analyses
behav_final$outcome_pred <- factor(behav_final$outcome)
behav_final_redcap$outcome_pred <- factor(behav_final_redcap$outcome)

# recode rt from s to ms
behav_final$rt <- behav_final$rt*1000
behav_final_redcap$rt <- behav_final_redcap$rt*1000

# set contrasts
contrasts(behav_final$outcome_pred) <- contr.treatment(2)
contrasts(behav_final_redcap$outcome_pred) <- contr.treatment(2)

contrasts(behav_final$reinforcer_type) <- abs(contr.treatment(2)-1)
contrasts(behav_final_redcap$reinforcer_type) <- abs(contr.treatment(2)-1)

redcap$aud_group <- factor(redcap$aud_group, levels = c("AUD", "HC"))
behav_final_redcap$aud_group <- factor(behav_final_redcap$aud_group, levels = c("AUD", "HC"))
contrasts(redcap$aud_group) <- abs(contr.treatment(2)-1)
contrasts(behav_final_redcap$aud_group) <- abs(contr.treatment(2)-1)

behav_final_redcap$screen_handeness <- factor(behav_final_redcap$screen_handeness)
behav_final_redcap$MRI <- factor(behav_final_redcap$MRI)
contrasts(behav_final_redcap$screen_handeness) <- contr.treatment(3, base=2)
#contrasts(behav_final_redcap$MRI) <- contr.treatment(1)

##### define se function #####

se <- function(x, na.rm = FALSE) {
  if (na.rm) {
    x <- x[!is.na(x)]       # remove NA, NaN, etc.
  }
  sd(x, na.rm = na.rm) / sqrt(length(x))
}

##### general settings #####

# number notation without exponentials
options(scipen = 50)
```

## Prepare dfs

```{r, echo=FALSE}
##### Create df with taste and craving ratings per subject and block (r_type long, rating timepoint wide format) #####

behav_rating <- behav_final %>%
  group_by(ID,reinforcer_type) %>%
  select(ID,reinforcer_type,ID_block,taste1, taste2, crave1, crave2) %>%
  distinct() %>%
  mutate(taste_diff=taste2-taste1,
         crave_diff=crave2-crave1,
         taste_mean = ((taste1 + taste2)/2),
         crave_mean = ((crave1 + crave2)/2))
behav_rating <- merge(behav_rating,redcap,by="ID",all.x = T) # merge with demographic data for linear mixed-effects regression

##### Create long dfs ######

behav_rating_long <- behav_rating %>%
  select(ID, aud_group, aud_sum, MRI_audit_sum, reinforcer_type, taste1, taste2, crave1, crave2) %>%
  pivot_longer(cols = c(taste1, taste2, crave1, crave2), names_to = "ratings")

behav_rating_long_taste <- behav_rating_long %>%
  filter(ratings %in% c("taste1", "taste2"))

behav_rating_long_crave <- behav_rating_long %>%
  filter(ratings %in% c("crave1", "crave2"))

# set contrasts

behav_rating_long_taste$ratings <- factor(behav_rating_long_taste$ratings)
contrasts(behav_rating_long_taste$ratings) <- contr.treatment(2)

behav_rating_long_crave$ratings <- factor(behav_rating_long_crave$ratings)
contrasts(behav_rating_long_crave$ratings) <- contr.treatment(2)

##### Create wide df containing demo data and taste and crave fmri covariates #####

behav_rating_wide <- behav_final_redcap %>%
  select(ID, reinforcer_type, taste1, taste2, crave1, crave2) %>%
  mutate(taste_diff = taste2-taste1,
         crave_diff = crave2-crave1) %>%
  distinct() %>%
  pivot_wider(names_from = reinforcer_type, values_from = c(taste1, taste2, taste_diff, crave1, crave2, crave_diff)) %>%
  rowwise() %>%
  mutate(taste_A = (taste1_A + taste2_A)/2,
         taste_J = (taste1_J + taste2_J)/2,
         crave_A = (crave1_A + crave2_A)/2,
         crave_J = (crave1_J + crave2_J)/2) %>%
  mutate(taste_AJ_diff = taste_A - taste_J,
         crave_AJ_diff = crave_A - crave_J) %>%
  mutate(taste_AJ = (taste_A + taste_J)/2,
         crave_AJ = (crave_A + crave_J)/2)

##### Add taste and craving diff AJ to behav_final and behav_final_redcap dfs #####

select_rating_vars <- behav_rating_wide %>%
  select(ID, taste_AJ, taste_AJ_diff, crave_AJ, crave_AJ_diff)

behav_final <- left_join(behav_final, select_rating_vars, by="ID")
behav_final_redcap <- left_join(behav_final_redcap, select_rating_vars, by="ID")

##### Correct #####

# get p correct per subject and block for plotting
df_c <- behav_final %>%
  group_by(ID,reinforcer_type) %>%
  summarise_at(vars(correct), list(p_correct = mean), na.rm=T)
df_c_rating <- merge(df_c,behav_rating,by=c("ID","reinforcer_type"))
df_c <- merge(df_c,redcap,by="ID") # merge with demographic data for linear mixed-effects regression

# get p correct per block and aud group and trial for plotting
df_c_block_trial_group <- behav_final_redcap %>%
  group_by(aud_group,reinforcer_type,trial_block) %>%
  dplyr::summarise(p_correct = mean(correct, na.rm = TRUE),
            ci_l = ci(correct, na.rm=TRUE)[2],
            ci_u = ci(correct, na.rm=TRUE)[3]
  )

##### Win-stay #####

# get p correct per subject and block for linear mixed-effects regression
df_win_stay <- behav_final %>%
  group_by(ID,reinforcer_type,taste,crave) %>%
  summarise_at(vars(stay,win_stay), list(p = mean), na.rm=T) %>%
  na.omit()
df_win_stay <- merge(df_win_stay,redcap,by="ID") # merge with demographic data for linear mixed-effects 

# get p correct per block and aud group and trial for plotting
df_win_stay_trial_group <- behav_final_redcap %>%
  group_by(aud_group,reinforcer_type,trial_block) %>%
  dplyr::summarise(p = mean(win_stay, na.rm = TRUE),
            ci_l = ci(win_stay, na.rm=TRUE)[2],
            ci_u = ci(win_stay, na.rm=TRUE)[3]
  )

##### No-win-switch #####

# get p correct per subject and block for linear mixed-effects regression
df_nowin_switch <- behav_final %>%
  group_by(ID,reinforcer_type,taste,crave) %>%
  summarise_at(vars(stay,nowin_switch), list(p = mean), na.rm=T) %>%
  na.omit()
df_nowin_switch <- merge(df_nowin_switch,redcap,by="ID") # merge with demographic data for linear mixed-effects 

# get p correct per block and aud group and trial for plotting
df_nowin_switch_trial_group <- behav_final_redcap %>%
  group_by(aud_group,reinforcer_type,trial_block) %>%
  dplyr::summarise(p = mean(nowin_switch, na.rm = TRUE),
            ci_l = ci(nowin_switch, na.rm=TRUE)[2],
            ci_u = ci(nowin_switch, na.rm=TRUE)[3]
  )

##### RT #####

# get rt per subject and block
df_rt <- behav_final %>%
  group_by(ID,reinforcer_type,taste,crave) %>%
  summarise_at(vars(rt), list(p = mean)) %>%
  na.omit()
df_rt <- merge(df_rt,redcap,by="ID") # merge with demographic data

# get p correct per block and aud group and trial for plotting
df_rt_trial_group <- behav_final_redcap %>%
  group_by(aud_group,reinforcer_type,trial_block) %>%
  dplyr::summarise(p = mean(rt, na.rm = TRUE),
            ci_l = ci(rt, na.rm=TRUE)[2],
            ci_u = ci(rt, na.rm=TRUE)[3]
  )

```

# Taste and craving rating

## Descriptive stats

```{r}

d_rating <- behav_rating %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('taste1','taste2','crave1','crave2','taste_diff','crave_diff', 'taste_mean', 'crave_mean'), .fns=
                   list('_mean' = mean,
                        '_se' = se,
                        '_min' = min,
                        '_max' = max),
                   na.rm=TRUE))

d_rating_nan <- behav_rating %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('taste1','taste2','crave1','crave2','taste_diff','crave_diff','taste_mean','crave_mean'), 
                          .fns=list('_na' = ~sum(is.na(.)))))
d_rating_nan

# alc AUD
stats <- d_rating[1,-1:-2] %>% gather(stat, val) %>%
  separate(stat, into = c("var", "stat"), sep = "__") %>%
  spread(stat, val) %>%
  mutate(across(c('max','mean','min','se'), round, 2))
stats

# alc HC
stats <- d_rating[2,-1:-2] %>% gather(stat, val) %>%
  separate(stat, into = c("var", "stat"), sep = "__") %>%
  spread(stat, val) %>%
  mutate(across(c('max','mean','min','se'), round, 2))
stats

# jui AUD
stats <- d_rating[3,-1:-2] %>% gather(stat, val) %>%
  separate(stat, into = c("var", "stat"), sep = "__") %>%
  spread(stat, val) %>%
  mutate(across(c('max','mean','min','se'), round, 2))
stats

# jui HC
stats <- d_rating[4,-1:-2] %>% gather(stat, val) %>%
  separate(stat, into = c("var", "stat"), sep = "__") %>%
  spread(stat, val) %>%
  mutate(across(c('max','mean','min','se'), round, 2))
stats
```

```{r}
# Correlation taste and craving ratings
cor.test(behav_rating_wide$taste_AJ_diff, behav_rating_wide$crave_AJ_diff, method="spearman")
cor.test(behav_final_redcap$taste, behav_final_redcap$crave, , method="spearman")
```

## Linear mixed-effects regression

### Taste ratings

#### Time effects

```{r}
m_taste_time <- lmer(value ~ 1 + reinforcer_type*aud_group*ratings + (1 + reinforcer_type + ratings |ID), 
                     data=behav_rating_long_taste,
                     control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_taste_time,
          dv.labels=c("m_taste_time"), digits=2, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))#

check_model(m_taste_time, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq") )
```

```{r}
m_taste_time_rob <- rlmer(value ~ 1 + reinforcer_type*aud_group*ratings + (1 + reinforcer_type + ratings |ID), 
                     data=behav_rating_long_taste,
                     control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_taste_time_rob,
          dv.labels=c("m_taste_time_rob"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

# CIs <- confintROB(m_taste_time_rob, parm=c(1:8), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_taste_time_rob.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_taste_time_rob.rds"))
CIs
```

```{r}
summary(emmeans(m_taste_time_rob, specs = pairwise ~ reinforcer_type|aud_group|ratings, lmer.df = "asymptotic", adjust = "bonf", ), infer=TRUE)
summary(emmeans(m_taste_time_rob, specs = pairwise ~ aud_group|reinforcer_type|ratings, lmer.df = "asymptotic", adjust = "bonf"), infer=TRUE)
summary(emmeans(m_taste_time_rob, specs = revpairwise ~ ratings|aud_group|reinforcer_type, lmer.df = "asymptotic", adjust = "bonf"), infer=TRUE)
```

#### Across both ratings

```{r}
m_taste <- lmer(value ~ 1 + reinforcer_type*aud_group + (1 + reinforcer_type| ID), 
                     data=behav_rating_long_taste,
                     control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_taste,
          dv.labels=c("m_taste"), digits=2, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

check_model(m_taste, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq") )
```

```{r}
m_taste_rob <- rlmer(value ~ 1 + reinforcer_type*aud_group + (1 + reinforcer_type| ID), 
                     data=behav_rating_long_taste,
                     control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_taste_rob,
          dv.labels=c("m_taste_rob"), digits=2, digits.re=2, df.method = "normal", 
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci = 0.95, CSS = css_theme("cells"))#

# CIs <- confintROB(m_taste_rob, parm=c(1:4), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_taste_rob.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_taste_rob.rds"))
CIs
```

```{r}
summary(emmeans(m_taste, specs = pairwise ~ reinforcer_type|aud_group, lmer.df = "satterthwaite", adjust = "bonf"), infer=TRUE)
summary(emmeans(m_taste, specs = pairwise ~ aud_group|reinforcer_type, lmer.df = "satterthwaite", adjust = "bonf"), infer=TRUE)
```

```{r}
plot_model(m_taste, type = "pred", terms = c("aud_group", "reinforcer_type"))
```

### Craving ratings

#### Time effects

```{r}
m_crave_time <- lmer(value ~ 1 + reinforcer_type*aud_group*ratings + (1 + reinforcer_type + ratings|ID), 
                     data=behav_rating_long_crave,
                     control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_crave_time,
          dv.labels=c("m_crave_time"), digits=2, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

check_model(m_crave_time, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq") )
```

```{r}
m_crave_time_rob <- rlmer(value ~ 1 + reinforcer_type*aud_group*ratings + (1 + reinforcer_type + ratings|ID), 
                     data=behav_rating_long_crave,
                     control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_crave_time_rob,
          dv.labels=c("m_crave_time_rob"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))
summary(m_crave_time_rob)

# CIs <- confintROB(m_crave_time_rob, parm=c(1:8), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_crave_time_rob.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_crave_time_rob.rds"))
CIs
```

```{r}
summary(emmeans(m_crave_time_rob, specs = pairwise ~ reinforcer_type|aud_group|ratings, lmer.df = "asymptotic", adjust = "bonf"), infer=TRUE)
summary(emmeans(m_crave_time_rob, specs = pairwise ~ aud_group|reinforcer_type|ratings, lmer.df = "asymptotic", adjust = "bonf"), infer=TRUE)
```

```{r}
plot_model(m_crave_time, type = "pred", terms = c("aud_group", "reinforcer_type"))
```

#### Across both ratings

```{r}
m_crave <- lmer(value ~ 1 + reinforcer_type*aud_group + (1+reinforcer_type|ID), 
                     data=behav_rating_long_crave,
                     control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_crave,
          dv.labels=c("m_crave"), digits=2, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

check_model(m_crave, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq") )
```

```{r}
m_crave_rob <- rlmer(value ~ 1 + reinforcer_type*aud_group + (1+reinforcer_type|ID), 
                     data=behav_rating_long_crave,
                     control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_crave_rob,
          dv.labels=c("m_crave_rob"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))#

# CIs <- confintROB(m_crave_rob, parm=c(1:4), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_crave_rob.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_crave_rob.rds"))
CIs
```

```{r}
summary(emmeans(m_crave_rob, specs = pairwise ~ reinforcer_type|aud_group, lmer.df = "asymptotic", adjust = "bonf"), infer=TRUE)
summary(emmeans(m_crave_rob, specs = pairwise ~ aud_group|reinforcer_type, lmer.df = "asymptotic", adjust = "bonf"), infer=TRUE)
```

## Plotting

### Taste per time point, group, reinforcer type

```{r}
fig_taste <- ggplot(behav_rating_long_taste, aes(x = ratings, y = value, fill = fct_rev(fct_infreq(reinforcer_type)))) +
  geom_violin() +
  geom_boxplot(aes(group=interaction(ratings,fct_rev(fct_infreq(reinforcer_type)))), 
               width=0.1, position=position_dodge(width = 0.9),
               size=0.8) + 
  facet_wrap(~fct_rev(fct_infreq(aud_group)), scales="fixed") +
  scale_x_discrete("Timepoint", labels=c('pre', 'post')) +
  scale_y_continuous("Taste rating") +
  theme_light(base_size=18, base_family = "Aptos") +
  theme(legend.position = "top") +
  scale_fill_brewer(name="Reinforcer type", 
                    labels=c("juice", "alcohol"),
                    palette = "Pastel1",
                    direction=-1)

fig_taste
```

### Craving per time point, group, reinforcer type

```{r}
fig_crave <- ggplot(behav_rating_long_crave, aes(x = ratings, y = value, fill = fct_rev(fct_infreq(reinforcer_type)))) +
  geom_violin() +
  geom_boxplot(aes(group=interaction(ratings,fct_rev(fct_infreq(reinforcer_type)))), 
               width=0.1, position=position_dodge(width = 0.9),
               size=0.8) + 
  facet_wrap(~fct_rev(fct_infreq(aud_group)), scales="fixed") +
  scale_x_discrete("Timepoint", labels=c('pre', 'post')) +
  scale_y_continuous("Craving rating") +
  theme_light(base_size=18, base_family = "Aptos") +
  theme(legend.position = "top") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("juice", "alcohol"),
                  palette = "Pastel1",
                  direction=-1)

fig_crave
```

### Combined plot

```{r}
fig_taste_crave <- ggarrange(fig_taste, fig_crave,
          labels = c("A", "B"),
          ncol = 2, nrow = 1,
          common.legend = TRUE, legend="bottom")
fig_taste_crave

```

# Correct choices

## Descriptive stats

```{r}
# per group and reinforcer type
df_c_stats <- behav_final_redcap %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('correct'), .fns=
                   list('_mean' = mean,
                        '_se' = se,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))
df_c_stats

df_c_stats_nan <- behav_final_redcap %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('correct'), .fns=
                   list('_na' = ~sum(is.na(.)))))
df_c_stats_nan

# per group
df_c_stats <- behav_final_redcap %>%
  group_by(aud_group) %>%
  dplyr::summarise(across(c('correct'), .fns=
                   list('_mean' = mean,
                        '_se' = se,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

df_c_stats

df_c_stats_nan <- behav_final_redcap %>%
  group_by(aud_group) %>%
  dplyr::summarise(across(c('correct'), .fns=
                   list('_na' = ~sum(is.na(.)))))

df_c_stats_nan

# per reinforcer type
df_c_stats <- behav_final_redcap %>%
  group_by(reinforcer_type) %>%
  dplyr::summarise(across(c('correct'), .fns=
                   list('_mean' = mean,
                        '_se' = se,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

df_c_stats

df_c_stats_nan <- behav_final_redcap %>%
  group_by(reinforcer_type) %>%
  dplyr::summarise(across(c('correct'), .fns=
                   list('_na' = ~sum(is.na(.)))))

df_c_stats_nan

# first trial only
# per group and reinforcer type
df_c_stats <- behav_final_redcap %>%
  group_by(reinforcer_type,aud_group) %>%
  filter(trial_block==1) %>%
  dplyr::summarise(across(c('correct'), .fns=
                   list('_mean' = mean,
                        '_se' = se,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))
df_c_stats
```

## Time effects

```{r}
m_correct_time_1 <- glmer(correct ~ 1 + reinforcer_type*aud_group*trial_block_centered + (1 + reinforcer_type + trial_block_centered | ID), 
                         data=behav_final_redcap, 
                         family = binomial, 
                         control=glmerControl(calc.derivs=FALSE))

tab_model(m_correct_time_1,
          dv.labels=c("m_correct_time_1"), digits=2, digits.re=2, show.est = T, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

check_model(m_correct_time_1, check=c("pp_check", "reqq", "qq"))

```

## Across all trials

```{r}
m_correct_1 <- glmer(correct ~ 1 + reinforcer_type*aud_group + (1 + reinforcer_type | ID), 
                         data=behav_final_redcap, 
                         family = binomial, 
                         control=glmerControl(calc.derivs=FALSE))

tab_model(m_correct_1,
          dv.labels=c("m_correct_1"), digits=2, digits.re=2, show.est = T, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

check_model(m_correct_1, check=c("pp_check", "reqq", "qq"))
```

## Controlling for covariates

### Determine correlation between % correct & taste

```{r}
# taste
lm_correct_taste <- glmer(correct ~ taste + (1 + taste| ID), 
                        data=behav_final_redcap, 
                        family = binomial,
                        control=glmerControl(calc.derivs=FALSE))

tab_model(lm_correct_taste,
          dv.labels=c("lm_correct_taste"), digits=2, digits.re=2, show.est = T, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

check_model(lm_correct_taste, check=c("pp_check", "reqq", "qq"))

if (sample == 'n56') {
  # age
  lm_correct_age <- glmer(correct ~ age + (1 | ID), 
                          data=behav_final_redcap, 
                          family = binomial,
                          control=glmerControl(calc.derivs=FALSE))
  
  tab_model(lm_correct_age,
            dv.labels=c("lm_correct_age"), digits=2, digits.re=2, show.est = T, df.method = "wald",
            show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))
  
  check_model(lm_correct_age, check=c("pp_check", "reqq", "qq"))
}

# smoking_days
lm_correct_smoking <- glmer(correct ~ BA_smoking_days + (1 | ID), 
                        data=behav_final_redcap, 
                        family = binomial,
                        control=glmerControl(calc.derivs=FALSE))

tab_model(lm_correct_smoking,
          dv.labels=c("lm_correct_smoking"), digits=2, digits.re=2, show.est = T, df.method = "wald",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

check_model(lm_correct_smoking, check=c("pp_check", "reqq", "qq"))
```

## Plotting

## Per group and reinforcer type

```{r}
fig_correct <- ggplot(df_c, aes(fct_rev(fct_infreq(reinforcer_type)), y = p_correct*100, fill=fct_rev(fct_infreq(reinforcer_type)))) +
  geom_violin() +
  geom_boxplot(width=0.1, size=0.8) + 
  facet_wrap(~fct_rev(fct_infreq(aud_group)), scales="fixed") +
  scale_y_continuous("% Correct choices", limits = c(0,100)) +
  theme_light(base_size=18, base_family = "Aptos") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        legend.position = "bottom") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("juice", "alcohol"),
                  palette = "Pastel1",
                  direction = -1)
fig_correct
```

## Correct choices over course of task

```{r}
fig_correct_time <- ggplot(df_c_block_trial_group, aes(x=trial_block, y=p_correct*100, group=fct_rev(fct_infreq(reinforcer_type)))) +
  geom_line(aes(color=fct_rev(fct_infreq(reinforcer_type))), linewidth=0.8) +
  geom_ribbon(aes(ymin = ci_l*100, ymax = ci_u*100, fill = fct_rev(fct_infreq(reinforcer_type))), alpha = 0.2) + 
  facet_wrap(~fct_rev(fct_infreq(aud_group)), scales="free_y") +
  scale_y_continuous("% Correct choices", limits = c(-50,175)) +
  scale_x_continuous("Trial") +
  theme_light(base_size=18, base_family = "Aptos") +
  theme(legend.position = "right") +
  scale_color_brewer(name="Reinforcer type", 
                  labels=c("juice", "alcohol"),
                  palette = "Pastel1",
                  direction = -1) +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("juice", "alcohol"),
                  palette = "Pastel1",
                  direction=-1)

fig_correct_time

```

# Reaction times

## Descriptive stats

```{r}
# per group and reinforcer type
df_rt_stats <- behav_final_redcap %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('rt'), .fns=
                   list('_mean' = mean,
                        '_se' = se,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))
df_rt_stats

df_rt_stats_nan <- behav_final_redcap %>%
  group_by(reinforcer_type,aud_group) %>%
  dplyr::summarise(across(c('rt'), .fns=
                   list('_na' = ~sum(is.na(.)))))
df_rt_stats_nan

# per group
df_rt_stats <- behav_final_redcap %>%
  group_by(aud_group) %>%
  dplyr::summarise(across(c('rt'), .fns=
                   list('_mean' = mean,
                        '_se' = se,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

df_rt_stats

df_rt_stats_nan <- behav_final_redcap %>%
  group_by(aud_group) %>%
  dplyr::summarise(across(c('rt'), .fns=
                   list('_na' = ~sum(is.na(.)))))

df_rt_stats_nan

# per reinforcer type
df_rt_stats <- behav_final_redcap %>%
  group_by(reinforcer_type) %>%
  dplyr::summarise(across(c('rt'), .fns=
                   list('_mean' = mean,
                        '_se' = se,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))

df_rt_stats

df_rt_stats_nan <- behav_final_redcap %>%
  group_by(reinforcer_type) %>%
  dplyr::summarise(across(c('rt'), .fns=
                   list('_na' = ~sum(is.na(.)))))

df_rt_stats_nan

# for first trial only
df_rt_stats <- behav_final_redcap %>%
  group_by(reinforcer_type,aud_group) %>%
  filter(trial_block==1) %>%
  dplyr::summarise(across(c('rt'), .fns=
                   list('_mean' = mean,
                        '_se' = se,
                        '_min' = min,
                        '_max' = max),
                   na.rm=T))
df_rt_stats
```

## Time effects

```{r}
m_rt_trial_1=lmer(rt~reinforcer_type*aud_group*trial_block_centered + (1 + reinforcer_type + trial_block_centered | ID),
                data=behav_final_redcap,
                control=lmerControl(calc.derivs=FALSE), 
                REML=F)

tab_model(m_rt_trial_1,
          dv.labels=c("m_rt_trial"), digits=5, digits.re=2, transform = NULL, show.est = T, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

check_model(m_rt_trial_1, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

```

```{r}
# robust estimation
m_rt_trial_1_robust=rlmer(rt~reinforcer_type*aud_group*trial_block_centered + (1 + reinforcer_type + trial_block_centered | ID),
                data=behav_final_redcap,
                control=lmerControl(calc.derivs=FALSE), 
                REML=F)

tab_model(m_rt_trial_1_robust,
          dv.labels=c("m_rt_trial_1_robust"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

if (sample == "n58") {
  CIs <- confintROB(m_rt_trial_1_robust, parm=c(1:8), level=0.95, method="Wald")
  CIs
} else {
  confintROB(m_rt_trial_1_robust, parm=c(1:8), level=0.95, method="boot", boot.type = "parametric")
}

```

```{r}
emm_options(opt.digits = FALSE)
mtrends <- emtrends(m_rt_trial_1, ~reinforcer_type|aud_group, var = "trial_block_centered", lmer.df = "satterthwaite", lmerTest.limit = 5702, adjust = NULL, infer=TRUE)
mtrends
as.data.frame(mtrends)$t.ratio
pairs(mtrends, adjust = "bonf", infer=TRUE)

mtrends <- emtrends(m_rt_trial_1, ~aud_group|reinforcer_type, var = "trial_block_centered", lmer.df = "satterthwaite", lmerTest.limit = 5702, adjust = NULL, infer=TRUE)
mtrends
pairs(mtrends, adjust = "bonf", infer=TRUE)
```

```{r}
plot_model(m_rt_trial_1, type = "pred", terms = c("trial_block_centered [all]", "reinforcer_type", "aud_group")) +
  theme_light(base_size = 14)
```

## Across all trials

```{r}
m_rt_1=lmer(rt~reinforcer_type*aud_group + (1 + reinforcer_type| ID),
                data=behav_final_redcap,
                control=lmerControl(calc.derivs=FALSE),
                REML=F)

tab_model(m_rt_1,
          dv.labels=c("m_rt"), digits=2, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

check_model(m_rt_1, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))
```

```{r}
# robust estimation
m_rt_1_robust=rlmer(rt~reinforcer_type*aud_group + (1 + reinforcer_type| ID),
                data=behav_final_redcap,
                control=lmerControl(calc.derivs=FALSE),
                REML=F)

tab_model(m_rt_1_robust,
          dv.labels=c("m_rt_1_robust"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

#plot(m_rt_1_robust)

#CIs <- confintROB(m_rt_1_robust, parm=c(1:4), level=0.95, method="boot", boot.type = "parametric")
#saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_rt_1_robust.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_rt_1_robust.rds"))
CIs
```

```{r}
print(summary(emmeans(m_rt_1_robust, specs = pairwise ~ reinforcer_type|aud_group, lmer.df = "asymptotic", adjust = "bonf"), infer=TRUE)$contrasts, digits=5)
print(summary(emmeans(m_rt_1_robust, specs = pairwise ~ aud_group|reinforcer_type, lmer.df = "asymptotic", adjust = "bonf"), infer=TRUE)$contrasts, digits=5)
```

```{r}
plot_model(m_rt_1_robust, type = "pred", terms = c("aud_group", "reinforcer_type")) +
  theme_light(base_size = 14)
```

## Controlling for covariates

### Determine correlation between % correct & taste

```{r}
# taste
lm_rt_taste <- lmer(rt ~ taste + (1 + taste | ID), 
                        data=behav_final_redcap, 
                        control=lmerControl(calc.derivs=FALSE), 
                        REML=F)

tab_model(lm_rt_taste,
          dv.labels=c("lm_rt_taste"), digits=2, digits.re=2, show.est = T, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

check_model(lm_rt_taste, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

lm_rt_taste_rob <- rlmer(rt ~ taste + (1 + taste | ID), 
                        data=behav_final_redcap, 
                        control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(lm_rt_taste_rob,
          dv.labels=c("lm_rt_taste_rob"), digits=2, digits.re=2, show.est = T, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

# CIs <- confintROB(lm_rt_taste_rob, parm=c(1:2), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_rt_taste_rob.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_rt_taste_rob.rds"))
CIs

if (sample == "n56") {
  # age
  lm_rt_age <- lmer(rt ~ age + (1 | ID), 
                          data=behav_final_redcap, 
                          control=lmerControl(calc.derivs=FALSE), 
                     REML=F)
  
  tab_model(lm_rt_age,
            dv.labels=c("lm_rt_age"), digits=2, digits.re=2, show.est = T, df.method = "satterthwaite",
            show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))
  
  check_model(lm_rt_age, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))
  
  lm_rt_age_rob <- rlmer(rt ~ age + (1 | ID), 
                        data=behav_final_redcap, 
                        control=lmerControl(calc.derivs=FALSE), 
                     REML=F)
  
  tab_model(lm_rt_age_rob,
          dv.labels=c("lm_rt_age_rob"), digits=2, digits.re=2, show.est = T, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

  confintROB(lm_rt_age_rob, parm=c(1:2), level=0.95, method="boot", boot.type = "parametric")

}

# smoking
lm_rt_smoking <- lmer(rt ~ BA_smoking_days + (1 | ID), 
                        data=behav_final_redcap, 
                        control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(lm_rt_smoking,
          dv.labels=c("lm_rt_smoking"), digits=2, digits.re=2, show.est = T, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

check_model(lm_rt_smoking, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

lm_rt_smoking_rob <- rlmer(rt ~ BA_smoking_days + (1 | ID), 
                        data=behav_final_redcap, 
                        control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(lm_rt_smoking_rob,
          dv.labels=c("lm_rt_smoking_rob"), digits=2, digits.re=2, show.est = T, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))
summary(lm_rt_smoking_rob)
# CIs <- confintROB(lm_rt_smoking_rob, parm=c(1:2), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_rt_smoking_rob.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_lm_rt_smoking_rob.rds"))
CIs

```

### Time effects

```{r}
m_rt_trial_1_controlled=lmer(rt~reinforcer_type*trial_block_centered*aud_group + taste + BA_smoking_days + (1 + reinforcer_type + trial_block_centered | ID),
                data=behav_final_redcap,
                control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_rt_trial_1_controlled,
          dv.labels=c("m_rt_trial_1_controlled"), digits=3, digits.re=2, transform = NULL, show.est = T, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

check_model(m_rt_trial_1_controlled, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

vif(m_rt_trial_1_controlled)
```

```{r}
m_rt_trial_1_controlled_rob=rlmer(rt~reinforcer_type*trial_block_centered*aud_group + taste + BA_smoking_days + (1 + reinforcer_type + trial_block_centered | ID),
                data=behav_final_redcap,
                control=lmerControl(calc.derivs=FALSE), 
                     REML=F)

tab_model(m_rt_trial_1_controlled_rob,
          dv.labels=c("m_rt_trial_1_controlled_rob"), digits=2, digits.re=2, transform = NULL, show.est = T, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))


if (sample == "n58") {
  CIs <- confintROB(m_rt_trial_1_controlled_rob, parm=c(1:10), level=0.95, method="Wald")
  CIs
} else {
  confintROB(m_rt_trial_1_controlled_rob, parm=c(1:10), level=0.95, method="boot", boot.type = "parametric")
}
```

```{r}
mtrends <- emtrends(m_rt_trial_1_controlled, ~reinforcer_type|aud_group, var = "trial_block_centered", lmer.df = "satterthwaite", lmerTest.limit = 5702)
pairs(mtrends, adjust = "bonf")

mtrends <- emtrends(m_rt_trial_1_controlled, ~aud_group|reinforcer_type, var = "trial_block_centered", lmer.df = "satterthwaite", lmerTest.limit = 5702)
pairs(mtrends, adjust = "bonf")
```

```{r}
plot_model(m_rt_trial_1_controlled, type = "pred", terms = c("trial_block_centered [all]", "reinforcer_type", "aud_group")) +
  theme_light(base_size = 14)
```

### Across all trials

```{r}
m_rt_1_controlled=lmer(rt~reinforcer_type*aud_group + taste + BA_smoking_days + (1 + reinforcer_type | ID),
                data=behav_final_redcap,
                control=lmerControl(calc.derivs=FALSE),
                REML=F)

tab_model(m_rt_1_controlled,
          dv.labels=c("m_rt_1_controlled"), digits=2, digits.re=2, df.method = "satterthwaite",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

check_model(m_rt_1_controlled, check=c("pp_check", "linearity",  "homogeneity",  "normality", "reqq", "qq"))

```

```{r}
m_rt_1_controlled_rob=rlmer(rt~reinforcer_type*aud_group + taste + BA_smoking_days + (1 + reinforcer_type | ID),
                data=behav_final_redcap,
                control=lmerControl(calc.derivs=FALSE),
                REML=F)

tab_model(m_rt_1_controlled_rob,
          dv.labels=c("m_rt_1_controlled_rob"), digits=2, digits.re=2, df.method = "normal",
          show.se=TRUE, show.stat=TRUE, show.df=TRUE, show.ci= 0.95,CSS = css_theme("cells"))

# CIs <- confintROB(m_rt_1_controlled_rob, parm=c(1:6), level=0.95, method="boot", boot.type = "parametric")
# saveRDS(CIs, file=file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_rt_1_controlled_rob.rds"))
CIs <- readRDS(file.path(project_path, "WP2_ILT_DATA/Behav/models_cis/CIs_m_rt_1_controlled_rob.rds"))
CIs

```

```{r}
summary(emmeans(m_rt_1_controlled_rob, specs = pairwise ~ reinforcer_type|aud_group, lmer.df = "asymptotic", adjust = "bonf"), infer=TRUE)
summary(emmeans(m_rt_1_controlled_rob, specs = pairwise ~ aud_group|reinforcer_type, lmer.df = "asymptotic", adjust = "bonf"), infer=TRUE)
```

```{r}
plot_model(m_rt_1_controlled, type = "pred", terms = c("aud_group", "reinforcer_type")) +
  theme_light(base_size = 14)
```

## Plotting

### Violin plot per aud group and reinforcer type

```{r}
fig_rt <- ggplot(df_rt, aes(fct_rev(fct_infreq(reinforcer_type)), y = p/1000, fill=fct_rev(fct_infreq(reinforcer_type)))) +
  geom_violin() +
  geom_boxplot(width=0.1, size=0.8) + 
  facet_wrap(~fct_rev(fct_infreq(aud_group)), scales="fixed") +
  scale_y_continuous("Response time (s)", limits = c(0,1.2)) +
  theme_light(base_size=18, base_family = "Aptos") +
  theme(axis.title.x=element_blank(),
      axis.text.x=element_blank(),
      axis.ticks.x=element_blank(),
      legend.position = "bottom") +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("juice", "alcohol"),
                  palette = "Pastel1",
                  direction = -1)

fig_rt
```

### RT over course of task

```{r}
fig_rt_time <- ggplot(df_rt_trial_group, aes(x=trial_block, y=p/1000, group=fct_rev(fct_infreq(reinforcer_type)))) +
  geom_line(aes(color=fct_rev(fct_infreq(reinforcer_type))), linewidth=0.8) +
  geom_ribbon(aes(ymin = ci_l/1000, ymax = ci_u/1000, fill = fct_rev(fct_infreq(reinforcer_type))), alpha = 0.2) + 
  facet_wrap(~fct_rev(fct_infreq(aud_group)), scales="free_y") +
  scale_y_continuous("Response time (s)", limits = c(0,1.2)) +
  scale_x_continuous("Trial") +
  theme_light(base_size=18, base_family = "Aptos") +
  theme(legend.position = "right") +
  scale_color_brewer(name="Reinforcer type", 
                  labels=c("juice", "alcohol"),
                  palette = "Pastel1",
                  direction = -1) +
  scale_fill_brewer(name="Reinforcer type", 
                  labels=c("juice", "alcohol"),
                  palette = "Pastel1",
                  direction = -1)

fig_rt_time

```

# Combined plots for publication

```{r}
# save combined plot
fig_behav_violin <- ggarrange(fig_correct, fig_rt,
          labels = c("A", "B"),
          ncol = 2, nrow = 1,
          common.legend = TRUE, legend="bottom")
fig_behav_violin

```

```{r}
# save combined plot
fig_behav <- ggarrange(fig_taste_crave, fig_correct_time, fig_rt_time,
          labels = c("A", "C", "D"),
          ncol = 1, nrow = 3,
          common.legend = TRUE, legend="bottom", heights = c(1.3,1,1))
fig_behav

#ggsave(file.path(project_path, "Manuscript/Initial_draft/Figures", paste("final_fig_behav_", sample, ".png", sep="")), width = 20, height =25, units='cm', dpi = 600, bg="white")
```
